%\documentclass[08pt,a4paper]{article}



%%% NOT RENDERING BECAUSE NEW COLOUR PACKAGE IS INCOMPATIBLE -- >.FIX LATER  %%%




%\usepackage{fontspec}/Users/josephbulbulia/Dropbox/00Bulbulia Pubs/2016/2016_WATTS_BBS_RESPONSE/2016 Norenzayan cultural evolution.pdf
%\usepackage{yfonts} 

%\usepackage{kpfonts}
%\usepackage[T1]{fontenc}
%\usepackage{setspace} 
%%\usepackage{color}
%\usepackage[usenames, dvipsnames]{xcolor}

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[dvipsnames]{xcolor}
%\bibliographystyle{babplain}
%\bibliographystyle{unsrt}
%\usepackage{etaremune}
%\usepackage{kpfonts}
\usepackage[T1]{fontenc}
%\usepackage{setspace} 
%%\usepackage{color}
%\usepackage[usenames, dvipsnames]{xcolor}

% USE THIS TO UNDO NUMBERING

%\makeatletter
%\renewenvironment{thebibliography}[1]
%     {\section*{\refname}%
%      \@mkboth{\MakeUppercase\refname}{\MakeUppercase\refname}%
%      \list{}%
%           {\setlength{\labelwidth}{0pt}%
%            \setlength{\labelsep}{0pt}%
%            \setlength{\leftmargin}{\parindent}%
%            \setlength{\itemindent}{-\parindent}%
%            \@openbib@code
%            \usecounter{enumiv}}%
%      \sloppyhttps://www.overleaf.com/project/5f064805fb993800018c8f25
%      \clubpenalty4000
%      \@clubpenalty \clubpenalty
%      \widowpenalty4000%
%      \sfcode`\.\@m}
%     {\def\@noitemerr
%       {\@latex@warning{Empty `thebibliography' environment}}%
%      \endlist}
%\makeatother
%







\renewcommand*{\refname}{} % no title for bibliography

\usepackage[official]{eurosym}
%\renewcommand*\sfdefault{uop}
%\renewcommand*\familydefault{\sfdefault} %% Only if the base font of the document is to be sans serif
%\usepackage[T1]{fontenc}


% DOCUMENT LAYOUT
\usepackage{geometry} 
\geometry{a4paper, textwidth=5.5in, textheight=8.5in, marginparsep=7pt, marginparwidth=.6in}
\setlength\parindent{0in}

% FONTS
%\usepackage{xunicode}
%\usepackage{xltxtra}
%\defaultfontfeatures{Mapping=tex-text} % converts LaTeX specials (``quotes'' --- dashes etc.) to unicode
%\setromanfont [Ligatures={Common}, Numbers={OldStyle}]{EurekaMonoOT}
%\setromanfont[Scale=1]{Latin Modern Roman}
%\setromanfont [Ligatures={Common}, Numbers={OldStyle}]{Avenir Next LT Pro}
%\setmonofont[Scale=.9]{Nitti} 
%\setsansfont[Scale=1]{Univers Next Pro} 
%\newfontfamily{\secfont}{Latin Modern Roman}%{Akzidenz-Grotesk BQ Medium}
%\newfontfamily{\subsecfont}{Latin Modern Roman}%{Akzidenz-Grotesk BQ Medium}
% ---- CUSTOM AMPERSAND
%\newcommand{\&}{{\fontspec[Scale=.9]{Avenir Next LT Pro}\selectfont\itshape\&}}%{Hoefler Text}
% ---- MARGIN YEARS
\usepackage{marginnote}
\newcommand{\years}[1]{\marginnote{\scriptsize #1}}
\renewcommand*{\raggedleftmarginnote}{}
\setlength{\marginparsep}{7pt}
\reversemarginpar

% HEADINGS
\usepackage{sectsty} 
%\usepackage[normalem]{ulem} 
%\sectionfont{nitti typewriter} %\mdseries\large\underline} 
%\subsectionfont{nitti typewriter cameo}         %\rmfamily\mdseries\scshape\normalsize} 
%\subsubsectionfont{nitti typewriter cameo}  %\bfseries\upshape\normalsize} 
\usepackage{graphicx}
% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR
%\usepackage[xetex, bookmarks, colorlinks, breaklinks, pdftitle={Joseph Bulbulia - vita},pdfauthor={Joseph Bulbulia}]{hyperref}  
%\hypersetup{linkcolor=blue,citecolor=blue,filecolor=black,urlcolor=blue} 
\usepackage{hyperref}
\hypersetup{
    colorlinks,%
    citecolor=green,%
    filecolor=magenta,%
    linkcolor=red,% 
    urlcolor=cyan
}
%-------------------------------------
%\setlength{\textwidth}{17cm} \setlength{\oddsidemargin}{-0.5cm}
%-------------------------------------
\usepackage{mdwlist}
\usepackage{geometry}

\usepackage{sectsty} 
%\usepackage[normalem]{ulem} 
%\sectionfont{\subsecfont} 
%\subsectionfont{\subsecfont} 
%\subsubsectionfont{\subsecfont} 

%\usepackage{titlesec}
%\definecolor{MSBlue}{rgb}{.204,.353,.541}
%\definecolor{MSLightBlue}{rgb}{.31,.506,.741}
%\newfontfamily\subsubsectionfont{Constantia Bold}
%\titleformat*{\section}{\large\subsubsectionfont}
%\titleformat*{\subsection}{\subsubsectionfont}
%\titleformat*{\subsubsection}{\subsubsectionfont}
%\fontsize{10pt}{12pt}
% Customize page headers
%\pagestyle{myheadings}
%\markright{\name}

\usepackage{microtype} 
\usepackage{enumerate}
%\usepackage{lmodern}
\usepackage{setspace}
%%\onehalfspacing

\pagestyle{empty}

%\usepackage{sectsty}
%\sectionfont{\rmfamily\mdseries\Large}
%\subsectionfont{\rmfamily\mdseries\itshape\large}

\begin{document}
\singlespacing
%\doublespacing
%\textbf{\Large Joseph Bulbulia}\\~\\


\subsubsection*{Joseph A.Bulbulia}
\small
Professor, School of Psychology\\
Faculty of Science\\
Victoria University of Wellington, New Zealand \\
Research Associate,
Max Planck Institute for the Science of Human History,
%Kahlaische Strasse 10\\https://www.overleaf.com/project/5fa8c033f67ba2cdc0753c6e
%D-07745 Jena, 
Germany
%\href{http://www.shh.mpg.de/2375/en}{http://www.shh.mpg.de/2375/en}\\
%\href{http://www.shh.mpg.de/252138/dlcepeople}{http://www.shh.mpg.de/252138/dlcepeople}\\~\\
\subsubsection*{Contact}
eml:~\href{mailto: joseph.bulbulia@vuw.ac.nz}{joseph.bulbulia@vuw.ac.nz}\\
\textsc{url}:~\href{https://josephbulbulia.netlify.app}{https://josephbulbulia.netlify.app}\\
orcid::\href{https://orcid.org/0000-0002-5861-2056}{https://orcid.org/0000-0002-5861-2056}

\subsubsection*{Work}
\years{$2020\to$ ~} Professor of Psychology, Victoria University, New Zealand \\
\years{2018$\to$2020} Maclaurin Goodfellow Chair, School of Humanities The University of Auckland \\
\years{2000$\to$2017} Lecturer$\to$Senior Lecturer$\to$Reader$\to$Professor of Religion, Victoria University
%%\hrule
\subsubsection*{Specialisation}
Religion, evolution, longitudinal well-being, methods.

\subsubsection*{Education}
\noindent
\years{2001}Princeton University, Ph.D. Religion (Program in Religion and Philosophy)\\
\years{1997}Princeton University, M.A. Religion (Program in Religion and Philosophy)\\
\years{1993}Harvard University, M.T.S. Religion\\
\years{1990}Holy Cross, A.B. Philosophy\\
\years{1988$\rightarrow$1989} Oxford University: Mansfield College (Matriculated, Visiting Student) (Philosophy, Politics, Economics)

\subsubsection*{Honours}	
\noindent
\years{2019}Appointment: Research Associate,  \href{https://www.shh.mpg.de/252138/dlcepeople}{Max Plank Institute for the Science of Human History}\\
\years{2018}Appointment Maclaurin Goodfellow Chair, University of Auckland\\	
\years{2016}Victoria University Research Excellence Award\\																											
\years{2014$\to$}Co-editor: \href{http://www.tandfonline.com/toc/rrbb20/current#.U_V-VoCSzmU}{Religion Brain \& Behavior}\\						
\years{2014$\to$2016}President:  \href{http://www.iacsr.com/iacsr/Home.html}{International Association for the Cognitive Science of Religion}\\
\years{2012$\to$2014} President Elect:  \href{http://www.iacsr.com/iacsr/Home.html}{International Association for the Cognitive Science of Religion}\\
\years{2013$\to$}Editorial Advisory Board: \href{http://www.zygonjournal.org}{Zygon: Journal of Religion and Science }\\
\years{2011$\to$}Editorial Advisory Board: \href{http://www.equinoxpub.com/index.php/JCSR}{Journal of The Cognitive Science of Religion}\\
\years{2010$\to$2012}Secretary General (elected):  \href{http://www.iacsr.com/iacsr/Home.html}{International Association for the Cognitive Science of Religion}\\
\years{2010$\to$2014}Editorial Advisory Board: \href{http://www.ibcsr.org/index.php?option=com_content&view=article&id=159&Itemid=89}{\em Religion, Brain \& Behavior}\\
\years{2010$\to$2012}Advisor: \href{http://evolution-of-religion.com/}{The Adaptive Logic of Religious Belief and Behaviour Group}\\
\years{2006$\to$}Distinguished Fellow: \href{http://teo.au.dk/forskning/aktuelt/religion/deltagere/principal/}{Religion Cognition and Culture Group, Aarhus University}\\
\years{2006$\to$2010}Executive Committee (elected): \href{http://www.iacsr.com/Home.html}{International Association for the Cognitive Science of Religion}\\
\years{2006} G\ae steprofessor: \href{http://teo.au.dk/en/research/current/cognition}{Religion, Cognition, Culture Group: Aarhus University}\\
\years{2000}Faculty Fellowship, Stevenson Hall: Princeton University\\
\years{1996$\to$1999}Assistant Master, Stevenson Hall: Princeton University\\
\years{1996}Melon Fellowship: Princeton University\\
\years{1996}Bowen Merit Award: Princeton University\\
\years{1990}Flatly Award (top philosophy graduate): Holy Cross\\
\years{1990}Phi Beta Kappa: Holy Cross
% \section*{Previous Employment}
% \noindent
%         	%\setlength{\parskip}{-.5pt}
%     	    % \setlength{\parsep}{-.5pt}
% 	\years{2017$\rightarrow$}Professor, Religious Studies: Victoria University\\    
% 	\years{2014$\rightarrow$2016}Associate Professor, Religious Studies: Victoria University\\
%     \years{2006$\rightarrow$2013}Senior Lecturer, Religious Studies: Victoria University\\
%     \years{2006}Guest Professor: Aarhus University, Denmark\\
%     \years{2000$\to$2005}Lecturer, Religious Studies: Victoria University\\
%     \years{2000}Assistant Professor, Philosophy: New Jersey City University\\
%     \years{1997$\to$1999}Assistant Master, Stevenson Hall: Princeton University\\
%     \years{1994$\to$1996}Preceptor, Department of Religion: Princeton University\\%} \par%}
    %-------



\subsubsection*{Publications}

Selected science publications in \textcolor{Orange}{orange}

Selected theory publications in \textcolor{Green}{green}

Selected overviews of the scientific research \textcolor{Purple}{purple}


\begin{thebibliography}{99}

\subsubsection*{2021}
\bibitem{doi:10.1080/2153599X.2021.1876333}
J.~Bulbulia, W.~J. Wildman, R.~Sosis, and U.~Schjoedt.
\newblock Announcing a new type of manuscript submission: the ``retake''.
\newblock {\em Religion, Brain \& Behavior}, 11(1):1--4, 2021.\href{https://www.tandfonline.com/doi/full/10.1080/2153599X.2021.1876333}{HERE}

\bibitem{shanaah2021hate}
S.~Shanaah, K.~Yogeeswaran, L.~Greaves, J.~A. Bulbulia, D.~Osborne, M.~U.
  Afzali, and C.~G. Sibley.
\newblock Hate begets warmth? the impact of an anti-muslim terrorist attack on
  public attitudes toward muslims.
\newblock {\em Terrorism and Political Violence}, pages 1--19, 2021.

\bibitem{van_tongeren_religious_2021}
D.~R. Van~Tongeren, C.~N. DeWall, Z.~Chen, C.~G. Sibley, and J.~Bulbulia.
\newblock Religious residue: {Cross}-cultural evidence that religious
  psychology and behavior persist following deidentification.
\newblock {\em Journal of Personality and Social Psychology}, 120(2):484--503,
  2021.



\subsubsection*{2020}


\bibitem{diwali2020} Piven, S. D., Fischer, R., Shaver, J. H., Mogan, R., Karl, J., Kesberg, R., Richardson, A., Singh, P., Tewari, S., \& {\bf Bulbulia, J.} (in press).
\newblock Kiwi Diwali: A Longitudinal Investigation of Perceived Social Connection Following a Civic Religious Ritual.
\newblock {\em Religion, Brain \& Behavior}.

\bibitem{SStronge2020} Stronge, S. J., {\bf Bulbulia, J.}, Davis, D. E., \& Sibley, C. G. (in press). 
\newblock Religion and the Development of Character: Personality Changes Before and After Religious Conversion and Deconversion. 
\newblock {\em Social Psychological and Personality Science}.


\bibitem{Sibley1-2020} Sibley, C. G., Afzalib, M. U., Satherley, N., Ejova, A., Stronge, S., Yogeeswaran, K., Grimshaw, M., Hawi, D., Mirnajafi, Z., Barlow, F., Milojev, P., Greaves, L. M., Kapeli, S., Zubielevitch, E., Hamley, L., Basabas, M. C., Wu, M. H., Howard, C., Lee, C. H. J., Huang, Y., Lockhart, C., Bahamondes, J., Manuela, S., Milfont, T. L., Perry, R., Sengupta, N. K., Overall, N. C., Shaver, J. H., Troughton, G., Osborne, D., \& {\bf Bulbulia, J.} (in press). 
\newblock Prejudice toward Muslims in New Zealand: Insights from the New Zealand Attitudes and Values Study.
\newblock {\em New Zealand Journal of Psychology}.


\bibitem{Slingerland-2020} Slingerland, E., Atkinson, Q. D., Ember, C. R., Sheehan, O., Muthukrishna, M., {\bf Bulbulia, J.}, \& Gray, R. D. (in press). 
\newblock Coding Culture: Challenges and Recommendations for Comparative Cultural Databases.
\newblock {\em Evolutionary Human Sciences}. 


\bibitem{greaves2020comparative}
\textcolor{Orange}{L.~M. Greaves, A.~Rasheed, S.~D'Souza, N.~Shackleton, L.~D. Oldfield, C.~G.
  Sibley, B.~Milne, and J.~Bulbulia.
\newblock Comparative study of attitudes to religious groups in new zealand
  reveals muslim-specific prejudice.
\newblock {\em K{\=o}tuitui: New Zealand Journal of Social Sciences Online},
  15(2):260--279, 2020.}



\bibitem{Fraser:2020aa}
G.~Fraser, Y.~Huang, K.~Robinson, M.~S. Wilson, J.~Bulbulia, and C.~G. Sibley.
\newblock New zealand pet owners' demographic characteristics, personality, and
  health and wellbeing: More than just a fluff piece.
\newblock {\em Anthrozo{\"o}s}, 33(4):561--578, 2020.


\bibitem{Fraser1-2020} Fraser, G., {\bf Bulbulia, J.}, Greaves, L., Wilson, M. S., \& Sibley, C. G. (in press). 
\newblock Coding responses to an open-ended gender measure in a New Zealand national sample.
\newblock {\em Journal of Sex Research}. 


\bibitem{Ejova2020} Ejova, A., Milojev, P., Worthington Jr, E. L., {\bf Bulbulia, J.}, \& Sibley, C. G. (in press). 
\newblock The Big Six personality traits and mental distress: Dynamic modelling in a population panel study reveals bi-directional relationships involving Neuroticism, Extraversion and Conscientiousness.
\newblock {\em Personality and Social Psychology Bulletin}. 

\bibitem{Ejova:2020aa} Ejova, A., Milojev, P., Worthington~Jr, E.~L. , Sibley, C.~G., and {\bf }Bulbulia. J.
\newblock Church attendance buffers against longer-term mental distress.
\newblock {\em Religion, Brain \& Behavior}, pages 1--16, 2020.


\bibitem{ShaverJ2020} \textcolor{Orange}{Shaver, J. H., Power, E.A., Purzycki, B. G, Watts, J., Sear, R., Shenk, M. K., Sosis, R., \& {\bf Bulbulia J.} (2020). 
\newblock Church attendance and alloparenting: an analysis of fertility, social support and child development among English mothers. 
\newblock {\em Phil. Trans. R. Soc. B}, 375:20190428.
\href{http://dx.doi.org/10.1098/rstb.2019.0428}{DOI: 10.1098/rstb.2019.0428}}


\bibitem{PSingh2020} Singh, P., Tewari, S., Kesberg, R., Karl, J. A., {\bf Bulbulia, J.}, \& Fischer, R. (2020). 
\newblock Time investments in rituals are associated with social bonding, affect and subjective health: a longitudinal study of Diwali in two Indian communities. 
\newblock {\em Phil. Trans. R. Soc. B}, 375:20190430.
\href{http://dx.doi.org/10.1098/rstb.2019.0430}{DOI: 10.1098/rstb.2019.0430}


\bibitem{Sibley2} Sibley, C. G., Greaves, L. M., Satherley, N., Wilson, M. S., Overall, N. C., Lee, C. H. J., Milojev, M., {\bf Bulbulia, J.}, Osborne, D., Milfont, T. L., Houkamau, C. A., Duck, I. M., Vickers-Jones, R., \& Barlow , F. K. (2020).
\newblock Effects of the COVID-19 pandemic and nationwide lockdown on trust, attitudes toward government, and well-being. 
\newblock {\em American Psychologist}.
\href{http://dx.doi.org/10.1037/amp0000662}{DOI: 10.1037/amp0000662}


\bibitem{Cohen-Zimerman} Cohen-Zimerman, S., Cristofori, I., Zhong, W., {\bf Bulbulia, J.}, Krueger, F., Gordon, B., \& Grafman, J. (2020).
\newblock Neural underpinning of a personal relationship with God and sense of control: A lesion-mapping study.
\newblock {\em Cognitive, Affective, \& Behavioral Neuroscience}.
\href{https://doi.org/10.3758/s13415-020-00787-4}{DOI: 10.3758/s13415-020-00787-4}


\bibitem{Grafman} \textcolor{purple}{ Grafman, J., Cristofori, I., Zhong, W., \& {\bf Bulbulia, J}. (2020).
\newblock The Neural Basis of Religious Cognition.
\newblock {\em Current Directions in Psychological Science}, 1--8.
\href{https://doi.org/10.1177/0963721419898183}{DOI: 10.1177/0963721419898183}}



\subsubsection*{2019}



\bibitem{this} {\bf Bulbulia, J.}, Troughton, G., Highland, B., \& Sibley, C. G.  (2019).
\newblock A National-Scale Typology of Orientations to Religion Poses New Challenges for The Cultural Evolutionary Study of Religious Groups. 
\newblock {\em Religion, Brain \& Behavior}, 1--13. 
\href{https://doi.org/10.1080/2153599X.2019.1678516}{DOI: 10.1080/2153599X.2019.1678516}


\bibitem{this} Stronge, S., Mok, T., Ejova, A., Lee, C., Zubielevitch, E., Yogeeswaran, K., Hawi, D., Osborne,~D., {\bf Bulbulia, J.}, \& Sibley, C. G. (2019).
\newblock Social Media Use is (Weakly) Related to Psychological Distress. 
\newblock {\em Cyberpsychology, Behavior, and Social Networking}, 22(9), 604--609.
\href{https://doi.org/10.1089/cyber.2019.0176}{DOI: 10.1089/cyber.2019.0176}


\bibitem{this} 
{\bf  Bulbulia, J.}, Wildman, W. J., Schjoedt, U., \& Sosis, R. (2019).
\newblock Religion, In praise of descriptive research.  
\newblock {\em Religion, Brain \& Behavior}, 9(3), 219--220. 
\href{https://doi.org/10.1080/2153599X.2019.1631630}{DOI: 10.1080/2153599X.2019.1631630}


\bibitem{Hawi} 
Hawi, D., Osborne, D., {\bf Bulbulia, J.}, \& Sibley, C. G. (2019). 
\newblock Terrorism anxiety and attitudes toward Muslims. 
\newblock {\em New Zealand Journal of Psychology}, 48(1), 80--89.


\bibitem{Ben:2019aa}
Highland, B. R., Troughton, G., Shaver, J. H., Barrett, J. L., Sibley, C. G., \&
{\bf Bulbulia,~J}. (2019).
\newblock  Attitudes to Religion Predict Warmth for Muslims in New Zealand.
\newblock {\em New Zealand Journal of Psychology},  48(1), 122--132.


\bibitem{Mogan:2019aa}
Mogan, ~R., {\bf Bulbulia, ~J.}, \& Fischer, ~R. (2019)
\newblock Joint action enhances cohesion and positive affect, but suppresses aspects of creativity when combined with shared goals.
\newblock {\em Frontiers in Psychology}, 9.


\bibitem{doi:10.1080/2153599X.2019.1558595}
Schjoedt,~U., Wildman, W.~J., Sosis, R., \& {\bf Bulbulia,~J}. (2019)
\newblock Vikings, virtual reality, and supernatural agents in predictive
  minds.
\newblock {\em Religion, Brain \& Behavior}, 9(1), 1--1.


\bibitem{Shaver:2019aa}
Shaver, J.~H., Sibley, C.~G., Sosis,~R., Galbraith,~D., \&  {\bf Bulbulia,~J}. (2019).
\newblock Alloparenting and religious fertility: A test of the religious
  alloparenting hypothesis.
\newblock {\em Evolution and Human Behavior}, 40(3), 315--324. 


\bibitem{Beheim:2019}
Beheim, B., Atkinson, Q., {\bf Bulbulia, J}., Gervais, W. M., Gray, R., Henrich, J., Lang, M., Monroe, M., Muthukrishna, M., Norenzayan, A., Purzycki, B., Shariff, A., Slingerland, E., Spicer, R., \& Willard, A. K. (2019).
\newblock Corrected analyses show that moralizing gods precede complex societies but serious data concerns remain. 
\href{https://doi.org/10.31234/osf.io/jwa2n}{DOI: 10.31234/osf.io/jwa2n}


\subsubsection*{2018}
\bibitem{roitto2018oxford}
{\bf Bulbulia., ~J.} (2018).
\newblock Ritual and cooperation.
\newblock In R.~Uro, J.~J. Day, and R.~Roitto (Eds.), {\em The Oxford
  Handbook of Early Christian Ritual}, (pp. 95-114). Oxford University Press. 


\bibitem{gervais2018analytic}
\textcolor{Orange}{Gervais, W.~M., van Elk, M., Xygalatas, D., McKay, R.~T., Aveyard, M., Buchtel,
  E.~E., Dar-Nimrod, I., Klocov{\'a}, E.~K., Ramsay, J.~E., Riekki, T., \& {\bf Bulbulia, J.} (2018).
\newblock Analytic atheism: A cross-culturally weak and fickle phenomenon?
\newblock {\em Judgment and Decision Making}, 13(3), 268--274.}
\href{https://www.dropbox.com/s/0sltfq9mtgzqlxm/Gervaisetal.2018AnalyticAtheism.pdf?dl=0}{PDF}%{https://www.dropbox.com/s/0sltfq9mtgzqlxm/Gervaisetal.2018AnalyticAtheism.pdf?dl=0}


\bibitem{Sosis:2018aa}
Sosis,~R., {\bf Bulbulia, ~J.}, Wildman, W.~J., \& Schjoedt,~U. (2018).
\newblock The fish that got away? human behavioral ecology and the study of religion. 
\newblock {\em Religion, Brain \& Behavior}, 8(4), 351--353. 
\href{https://doi.org/10.1080/2153599X.2018.1523608}{DOI: 10.1080/2153599X.2018.1523608}
%\href{DOI: 10.1080/2153599X.2018.1523608}{https://doi.org/10.1080/2153599X.2018.1523608}


\bibitem{Shaver:2018asd}
Shaver, J. H., Sibley, C. G., \& {\bf Bulbulia, J.} (2018).
\newblock Are contemporary {C}hristian {N}ew {Z}ealanders committed to peace?
\newblock In Fountain, P. and Troughton, G., (Eds.), {\em Pursuing Peace in
  Godzone: Christianity and the Peace Tradition in New Zealand}, (pp. 194--205). Wellington: Victoria University Press.
\href{https://www.dropbox.com/s/2gklu6owh2yypgs/PPIGShaverBulbulia.pdf?dl=0}{PDF}


\bibitem{watts2018christianity}
\textcolor{Orange}{Watts, J., Sheehan, O., {\bf Bulbulia, J.}, Gray, R.~D., \& Atkinson, Q.~D. (2018).
\newblock Christianity spread faster in small, politically structured societies.
\newblock {\em Nature Human Behaviour}, 2(8), 559--564.}
\href{https://doi.org/10.1038/s41562-018-0379-3}{DOI: 10.1038/s41562-018-0379-3}


\bibitem{watts2018} 
Watts, J., Gray, R., \& {\bf Bulbulia, J.} (2018). 
\newblock The New Collaborative Scientific Study of Religious History. 
\newblock In A. K. Petersen, I. S. Gilhus, L. H. Martin, J. S. Jensen, and J. Sorensen (Eds.), {\em Evolution, Cognition, and the History of Religion: A New Synthesis}, (pp. 62--80). BRILL. 
\href{https://www.dropbox.com/s/wr5nq9ygiybspfp/WattsGrayAndBulbulia.pdf?dl=0}{PDF}


\bibitem{wildman2018god}
Wildman, W.~J., Schjoedt, U., Sosis, R., \& {\bf Bulbulia, J.} (2018).
\newblock ``God is watching you''{\ldots} and might be influencing your brain, too. 
\newblock {\em Religion, Brain \& Behavior}, 8(3), 263--264.
\href{https://doi.org/10.1080/2153599X.2018.1486619}{DOI:~10.1080/2153599X.2018.1486619}


\bibitem{doi:0}
Zhong, W., Krueger, F., Wilson, M., {\bf Bulbulia, J.}, \& Grafman, J. (2018). 
\newblock Prefrontal brain lesions reveal magical ideation arises from enhanced religious experiences. 
\newblock {\em Peace and Conflict: Journal of Peace Psychology}, 24(2), 245--249. 
\href{http://dx.doi.org/10.1037/pac0000336}{DOI: 10.1037/pac0000336}



\subsubsection*{2017}


\bibitem{10.1080/2153599X.2017.1314409}
Sosis, R., Schjoedt, U., {\bf Bulbulia, J}., \& Wildman, W. J. (2017).
\newblock Wilson’s 15-year-old cathedral.
\newblock {\em Religion, Brain \& Behavior}, 7(2), 95--97.
\href{https://doi.org/10.1080/2153599X.2017.1314409}{DOI: 10.1080/2153599X.2017.1314409}


\bibitem{doi:1}
Gervais, W. M, Xygalatas, D., McKay, R.T.,  van Elk, M., Buchtel, E., Aveyard, M., Schiavone S. R.,  Dar-Nimrod, I.,  Svedholm-H{\"a}kkinen, A. M., Riekki, T., Kundtov{\'a}, E. K.,  Ramsay, J. E., \& {\bf Bulbulia, J.} (2017).
\newblock Global evidence of extreme intuitive moral prejudice against atheists.
\newblock {\em Nature Human Behaviour}, 1, Article number: 0151. 
\href{https://doi.org/10.1038/s41562-017-0151}{DOI: 10.1038/s41562-017-0151}


\bibitem{doi:2} 
Shaver, J., Fraser, G.,\&  {\bf Bulbulia. J.} (2017). 
\newblock Charismatic Signaling: How religion stabilizes cooperation and entrenches inequality. 
\newblock In J. Liddle and T. Shackelford, (Eds.), {\em Oxford Handbook of Evolutionary Perspectives on Religion},  Oxford: Oxford University Press. 
\newblock \href{https://doi.org/10.1093/oxfordhb/9780199397747.013.17}{DOI:~10.1093/oxfordhb/9780199397747.013.17}
\href{https://www.dropbox.com/s/bnxz7r89jdt93uj/oxfordhb-9780199397747-e-17.pdf?dl=0}{PDF}
% Link: http://www.oxfordhandbooks.com/view/10.1093/oxfordhb/9780199397747.001.0001/oxfordhb-9780199397747-e-17?rskey=uxDpbJ&result=1


\bibitem{}{\bf Bulbulia, J.}, Fraser, G., Watts, J., \& Shaver, J. H. (2017). 
\newblock Can honest signaling theory clarify religion's role in the evolution of social inequality? 
\newblock {\em Religion, Brain \& Behavior}, 7(4), 285--288.


\bibitem{doi:0}{\bf Bulbulia, J.} (2017). 
\newblock Anthropology: Tradition's hidden economy. 
\newblock {\em Nature Human Behaviour}, 1, Article number: 0070. 
\href{https://doi.org/10.1038/s41562-017-0070}{DOI: 10.1038/s41562-017-0070}


\bibitem{doi:0}\textcolor{Purple}{
Mogan, R., Fischer, R., \& {\bf Bulbulia, J.} (2017). 
\newblock To be in synchrony or not? A meta-analysis of synchrony's effects on behavior, perception, cognition and affect.
\newblock {\em Journal of Experimental Social Psychology}, 72, 13--20.}


\bibitem{doi:0}
Shaver J. H, Sibley C. G, Osborne D., \& {\bf Bulbulia J.} (2017).
\newblock  News exposure predicts anti-Muslim prejudice. 
\newblock {\em PLoS ONE} 12(3), pe0174606. 
\href{https://doi.org/10.1371/journal.pone.0174606}{DOI:~10.1371/journal.pone.0174606}



\bibitem{Sibley:2016}
Sibley C.~G.,~Robertson, A., Osborne, D., Huang, Y., Milojev, P., Greaves, L., Houkamau, C.~A., {\bf Bulbulia, J.}, \& Barlow,~F. K. (2017).
\newblock Bias and tracking accuracy in voting projections using the {N}ew
  {Z}ealand {A}ttitudes and {V}alues Study.
\newblock {\em Political Science}, 69(1), 16--34.
 \href{https://doi.org/10.1080/00323187.2017.1321589}{DOI:~10.1080/00323187.2017.1321589}


\bibitem{doi:10.1080/2153599X.2017.1385202}
Sosis, R., Wildman, W.~J., {\bf Bulbulia, J.}, \& Schjoedt, U. (2017).
\newblock Hilbert problems in the scientific study of religion.
\newblock {\em Religion, Brain \& Behavior}, 7(4), 277--278.
%\href{https://www.dropbox.com/s/70e2988hk66wjr7/Hilbert%20Problems%20in%20the%20scientific%20study%20of%20religion.pdf?dl=0}{DOI:~10.1080/2153599X.2017.1385202}


\bibitem{doi:10.1080/2153599X.2017.1267953}
Sosis, R., {\bf Bulbulia, J.}, Wildman, W.~J., \& Schjoedt, U. (2017).
\newblock Religion, Brain \& Behavior's seventh year.
\newblock {\em Religion, Brain \& Behavior}, 7(1), 1--2.
\href{https://doi.org/10.1080/2153599X.2017.1267953}{DOI: 10.1080/2153599X.2017.1267953}
%\href{https://www.dropbox.com/s/yyprgw72lzs1p04/Religion%20Brain%20Behavior%20s%20seventh%20year.pdf?dl=0}{PDF}
\href{https://www.dropbox.com/s/ywxsyerusw7s59w/tandf_rrbb207_1.bib?dl=0}{BIB}


\bibitem{doi:10.1080/2153599X.2017.1368208}
Wildman, W. J., {\bf Bulbulia J.}, Sosis R., \& Schjoedt, U. (2017). 
\newblock  Models, simulations, abstractions, and insights.
{\em Religion, Brain \& Behavior},  7(3),  175--177.
%\href{https://www.dropbox.com/s/c5hhuzr5tkhkc49/Models%20simulations%20abstractions%20and%20insights.pdf?dl=0}{PDF}


\bibitem{doi.org/10.1016/j.neuropsychologia.2017.04.009}
Zhong, W., Cristofori, I., {\bf Bulbulia, J.}, Krueger, F., \& Grafman, J. (2017). 
\newblock Biological and cognitive underpinnings of religious fundamentalism. 
\newblock {\em Neuropsychologia}, 100, 18--25.
\href{https://doi.org/10.1016/j.neuropsychologia.2017.04.009}{DOI:~10.1016/j.neuropsychologia.2017.04.009}


\bibitem{doi.org/10.1007/s10508-017-1047-9}
Greaves, L. M., Barlow, F. K., Lee, C., Matika, C. M., Wang, W., Lindsay, C., Case, C., Sengupta, N. K., Huang, Y., Cowie, L. J., Stronge, S., Storey, M., Souza,  L., Manuela, S., Hammond, M. D., Milojev, P., Townrow, C. S., Muriwai, E., Satherly, N., Fraser, G., West-Newman, T., Houkamau, C., {\bf Bulbulia, J.}, Osborne, D., Wilson, M. S., \& Sibley, C. G.  (2017). 
\newblock Corrigendum to: The Diversity and Prevalence of Sexual Orientation Self-Labels in a New Zealand National Sample (Greaves et al., 2017). 
\newblock {\em Archives of Sexual Behavior}, 46, 2209–2210.
\href{ https://doi.org/10.1007/s10508-017-1063-9}{DOI: 10.1007/s10508-017-1063-9}


\subsubsection*{2016} 



%%% LARA PUB
%%% SHAVER CHAPTER
%%% OTHER CHAPTER
%%% 

\bibitem{Wildman:2016}
Wildman, W.J., Sosis, R., {\bf Bulbulia, J}., \& Spezio, M. L. (2016).
\newblock Critical Self-Correction
\newblock {\em Religion, Brain \& Behavior}, 6(2), 93--94. 
\href{https://doi.org/10.1080/2153599X.2016.1171062}{DOI: 10.1080/2153599X.2016.1171062}


\bibitem{Bulbulia:2016aa}
{\bf Bulbulia, J.}, Spezio, M., Sosis, R., \& Wildman, W. J.  (2016).
\newblock Standards for Publishing in Religion, Brain \& Behavior.
\newblock {\em Religion, Brain \& Behavior}, 6(4), 275--277. 
\href{http://dx.doi.org/10.1080/2153599X.2016.1227123}{DOI:~10.1080/2153599X.2016.1227123 }


\bibitem{greaves2016diversity}
Greaves, L. M., Barlow, F. K., Lee, C., Matika, C. M., Wang, W., Lindsay, C., Case, C., Sengupta, N. K., Huang, Y., Cowie, L. J., Stronge, S., Storey, M., Souza, L., Manuela, S., Hammond, M. D., Milojev, P., Townrow, C. S., Muriwai, E.,  Satherly, N.,   Fraser, G., West-Newman, T., Houkamau, C., {\bf Bulbulia, J.},  Osborne, D., Wilson, M. S., \& Sibley, C. G. (2017). 			
\newblock The diversity and prevalence of sexual orientation self-labels in a New Zealand national sample.									
\newblock {\em Archives of Sexual Behavior}, 46(5), 1325-1336. 												 
%\href{}{PDF} 
\href{https://doi.org/10.1007/s10508-016-0857-5}{DOI: 10.1007/s10508-016-0857-5}
\href{https://www.dropbox.com/s/gj05gm54am7tos7/2016.sxorient.bib?dl=0}{BIB}


\bibitem{Shaver:2016b}
Shaver, J.~H., \& {\bf Bulbulia, J.} (2016).
\newblock Signaling theory and religion.
\newblock In N. K Clements (Ed.), {\em Religion: Mental Religion}, (pp. 101--117). Macmillan
  Interdisciplinary Handbooks. 
\href{https://www.dropbox.com/s/3csna1dy4vbib92/Signaling_Theory_and_Religion.pdf?dl=0}{PDF} \href{https://www.dropbox.com/s/p4b2hzshwuk2q9u/2016.Sh.bul.STR.bib?dl=0}{BIB}


\bibitem{Shaver:2016a}
\textcolor{Orange}{Shaver, J.~H., Troughton, G., Sibley, C.~G., \& {\bf Bulbulia, J.} (2016).
\newblock Religion and the unmaking of prejudice toward muslims: Evidence from
  a large national sample.
\newblock {\em PLoS ONE}, 11(3),1--25.}
\href{https://www.dropbox.com/s/jw4r962hchojfvr/journal.pone.0150209.PDF?dl=0}{PDF} %\href{https://www.dropbox.com/s/p05yrm3s8u33ngr/10.1371%252Fjournal.pone.0150209.bib?dl=0}{BIB}


\bibitem{doi:10.1080/2153599X.2015.1109787}
Sosis, R., Spezio, M.~L., {\bf Bulbulia, J.}, \& Wildman, W.~J. (2016). Editorial:
\newblock The peer reviewer dilemma: how to appreciate the underappreciated.
\newblock {\em Religion, Brain \& Behavior}, 6(1), 1--3. 
%\href{https://www.dropbox.com/s/h2h90rcmycc5dco/2153599x%252E2015%252E1109787.pdf?dl=0}{PDF} 
%\href{}{BIB}


\bibitem{spezio2016religion}
Spezio, M.~L., Wildman, W.~J., Sosis, R., \& {\bf Bulbulia, J.} (2016). Editorial: 
\newblock Religion and emotion.
\newblock {\em Religion, Brain \& Behavior}, 5(3), 185--187.
%\href{https://www.dropbox.com/s/8zkvkrknib497tg/Religion%20and%20Emotion.pdf?dl=0}{PDF} %\href{https://www.dropbox.com/s/1oam4k5mw8gq8lr/Spez.ReligionEmotion.bib?dl=0}{BIB}


\bibitem{Watts:2016}
Watts, J., {\bf Bulbulia, J.}, Gray, R., \& Atkinson, Q.~D. (2016).
\newblock Clarity and causality needed in claims about big gods.
\newblock {\em Behavior and Brain Sciences}, 39, 41--42.
\href{https://www.dropbox.com/s/xag576vua0i80gq/2016WattsBBSResponseBigGods.pdf?dl=0}{PDF} \href{https://www.dropbox.com/s/71veqhxsq84ufao/wattsEtAl.2016.BigGodsResponse.bib?dl=0}{BIB}


\bibitem{Watts:2016aa}
\textcolor{Orange}{Watts, J., Sheehan, O., Atkinson, Q.~D., {\bf Bulbulia, J.}, \& Gray, R. (2016).
\newblock Ritual human sacrifice promoted and sustained the evolution of
  stratified societies.
\newblock {\em Nature}, 532, 228--231.}
\href{https://www.dropbox.com/s/e5avan4ex1nkgi6/nature17159.pdf?dl=0}{PDF}



\subsubsection*{2015} 


\bibitem{Satherley:2015}
Satherley, N., Milojev, P., Greaves, L. M., Huang, Y., Osborne, D., {\bf Bulbulia, J}., \& Sibley, C. G. (2015).
\newblock Scales for Sense of Belonging and Support [Database record].
\newblock APA PsycTests.
\href{https://doi.org/10.1037/t41438-000}{DOI: 10.1037/t41438-000}


\bibitem{Bulbulia:2014a}
\textcolor{Orange}{{\bf Bulbulia, J.}, Troughton, G., Greaves, L., Milfont, T.~L., Botera, C., Gray, R., \& Sibley,~C.~G. (2015).
\newblock To burn or to save? the opposing functions of reading scripture on
  environmental intentions.
\newblock {\em Religion, Brain \& Behavior}, 6(4), 278--289. }
%\href{https://www.dropbox.com/s/vl9bz550cc46s9g/2153599x%252e2015%252e1026926.pdf?dl=0}{PDF}
%\href{https://www.dropbox.com/s/rolzpckwfegaceb/205.bulbulia.burnsave.bib?dl=0}{BIB}


\bibitem{Bulbulia:2015aa}
{\bf Bulbulia, J.}, Shaver, J., Greaves, L., Sosis, R., \& Sibley, C.~G. (2015).
\newblock Religion and parental cooperation: an empirical test of {S}lone's
  sexual signaling model.
\newblock In Slone, D. and Van~Slyke, J., (Eds.), {\em The Attraction of
  Religion: A Sexual Selectionist Account}, (pp. 29--62). Bloomsbury Press. 
%\href{https://www.dropbox.com/s/6txkkawrhpirwcg/2014.OCT.30.Chapter2%28Bulbulia%20et%20al%29_w_comments%20copy.pdf?dl=0}{PDF} %\href{https://www.dropbox.com/s/7k3pm0nmtriso3b/2015.Bul.Parenting.bib?dl=0}{BIB}
 

\bibitem{doi:10.1080/2153599X.2015.1084470}
{\bf Bulbulia, J.}, Wildman, W.~J., Sosis, R., \& Spezio, M.~L. (2015). Editorial:
\newblock What are "the Hilbert Problems'' in the study of religion?
\newblock {\em Religion, Brain \& Behavior}, 5(4), 263--265. 
\href{https://doi.org/ 10.1080/2153599X.2015.1084470}{DOI:~10.1080/2153599X.2015.1084470}
%\href{https://www.dropbox.com/s/h5t7fexoibjaghm/2153599x%252E2015%252E1084470.pdf?dl=0}{PDF} \href{https://www.dropbox.com/s/5dp90zz5c6y6lif/tandf_rrbb205_263.bib?dl=0}{BIB}


\bibitem{Cristofori:2016aa}
\textcolor{Orange}{Cristofori, I., {\bf Bulbulia, J.}, Shaver, J.~H., Wilson, M., Krueger, F., \& Grafman, J. (2016).
\newblock Neural correlates of mystical experience.
\newblock {\em Neuropsychologia}, 80, 212--220. }
%\href{https://www.dropbox.com/s/uycwz4jt4d4n8tk/Cristofori%20et%20al_Neuropsychologia2016.pdf?dl=0}{PDF} \href{https://www.dropbox.com/s/xyrhei2v3fay7wi/neuralcorrelates.bib?dl=0}{BIB}
 

\bibitem{Greaves:2015ab}
Greaves, L.~M., Milojev, P., Huang, Y., Stronge, S., Osborne, D., {\bf Bulbulia, J.}, Grimshaw, M., \& Sibley, C.~G. (2015).
\newblock Regional differences in the psychological recovery of Christchurch residents following the 2010/2011 earthquakes: A longitudinal study.
\newblock {\em PLoS ONE}, 10(5), e0124278. 
\href{https://www.dropbox.com/s/5rb1nqsw4eiks05/journal.pone.0124278.pdf?dl=0}{PDF} %\href{https://www.dropbox.com/s/31mqt3g816p55yi/info%253Adoi%252F10.1371%252Fjournal.pone.0124278.bib?dl=0}{BIB}


\bibitem{Graeves:2015aa}
Greaves, L.~M., Cowie, L., Fraser, G., Muriwai, E., Zdrenka, M., Huang, Y., Milojev, P., Osborne, D., {\bf Bulbulia, J.}, Wilson, M.~S., Liu, J., Clouston, A., \& Sibley, C.~G. (2015).
\newblock Regional differences and similarities in the personality of {N}ew {Z}ealanders.
\newblock {\em New Zealand Journal of Psychology}, 44(1), 4--16.
%\href{https://www.dropbox.com/s/pwv3wtr3w0le0wx/NZJP-Volume-44-No%20-1-20151.pdf?dl=0}{PDF}


\bibitem{Hoverd:2015aa}
Hoverd, W.~J., {\bf Bulbulia, J.}, Partow, N., \& Sibley, C.~G. (2015).
\newblock Forecasting religious change: a Bayesian model predicting
  proportional Christian change in New Zealand.
\newblock {\em Religion, Brain \& Behavior}, 5(1), 15--23. 
%\href{https://www.dropbox.com/s/1q7aqj7fs1vw4po/2153599x%252E2013%252E824497.pdf?dl=0}{PDF} \href{https://www.dropbox.com/s/av6jrhlhgdgcz86/tandf_rrbb205_15.bib?dl=0}{BIB}


\bibitem{Satherley:2015}
Satherley, N., Milojev, P., Greaves, L.~M., Huang, Y., Osborne, D., {\bf Bulbulia, J.}, \& Sibley, C.~G. (2015).
\newblock Demographic and psychological predictors of panel attrition: Evidence
  from the {N}ew {Z}ealand {A}ttitudes and {V}alues {S}tudy.
\newblock {\em PLoS ONE}, 10(3), e0121950. 
\href{https://www.dropbox.com/s/t5j2oyalr97f5aj/journal.pone.0121950.pdf?dl=0}{PDF} %\href{https://www.dropbox.com/s/ubzbz0xp6cwvwe0/info%253Adoi%252F10.1371%252Fjournal.pone.0121950.bib?dl=0}{BIB}


\bibitem{Spezion:2015}
Spezio, M.~L., {\bf Bulbulia, J.}, Wildman, W.~J.,\& Sosis, R. (2015). Editorial:
\newblock Religion, {SCAN}, and developing standards of inquiry.
\newblock {\em Religion, Brain \& Behavior}, 5(3),179--181.
%\href{https://www.dropbox.com/s/ikn5lqnyht5tz2s/2153599x%252E2015%252E1053690.pdf?dl=0}{PDF} \href{https://www.dropbox.com/s/xdtdqvw7m93rfzj/2015.speziobul.bib?dl=0}{BIB}
 

\bibitem{Sibley:2015aa}
Sibley, C.~G., \& {\bf Bulbulia, J.} (2015).
\newblock Charity explains differences in life satisfaction between religious
  and secular New Zealanders.
\newblock {\em Religion, Brain \& Behavior}, 5(2), 91--100.
%\href{https://www.dropbox.com/s/1vhnxqmw9hdlf5i/use.2153599x%252E2014%252E899509.pdf?dl=0}{PDF} \href{https://www.dropbox.com/s/1vq0u6b94sn50ut/use.tandf_rrbb205_91-2.bib?dl=0}{BIB}


\bibitem{Watts:2015aa}
\textcolor{Orange}{Watts, J., Greenhill, S.~J., Atkinson, Q.~D., Currie, T.~E., {\bf Bulbulia, J.}, \&
  Gray, R.~D. (2015).
\newblock Broad supernatural punishment but not moralizing high gods precede
  the evolution of political complexity in Austronesia.
\newblock {\em Proceedings of the Royal Society of London B: Biological
  Sciences}, 282(1804), 20142556--20142556.
\href{https://doi.org/10.1098/rspb.2014.2556}{DOI:10.1098/rspb.2014.2556}}
\href{https://www.dropbox.com/s/kx3br0orme0dztr/20142556.full.pdf?dl=0}{PDF} \href{https://www.dropbox.com/s/xlj936kpv3obvhc/rspb20142556supp1.pdf?dl=0}{SUPPLEMENT} 
\href{https://www.dropbox.com/s/jpwqqqtqiomvnqe/broad-supernatural-punishment-but-not-moralizing-high-gods-precede-the-evolution-of-political-complexity-in-austronesia.bib?dl=0}{BIB} 


\bibitem{10.1371/journal.pone.0136783}
\textcolor{Orange}{Watts, J., Sheehan, O., Greenhill, S.~J., Gomes-Ng, S., Atkinson, Q.~D.,
  {\bf Bulbulia, J.}, \& Gray, R.~D. (2015).
\newblock Pulotu: Database of Austronesian supernatural beliefs and practices. 
\newblock {\em PLoS ONE}, 10(9):e0136783.}
 \href{https://www.dropbox.com/s/x7nw0co4clo1lkb/journal.pone.0136783.pdf?dl=0}{PDF}
% \href{https://www.dropbox.com/s/upsqwbn0bv3pgqd/info%253Adoi%252F10.1371%252Fjournal.pone.0136783.bib?dl=0}{BIB}


\bibitem{Wildman:2015aa}
Wildman, W.~J., Sosis, R., Spezio, M.~L., \& {\bf Bulbulia, J.} (2015). Editorial:
\newblock The emerging psychology of religion.
\newblock {\em Religion, Brain \& Behavior}, 5(2), 89--90. 
\href{https://www.dropbox.com/s/wv6tlmlec5r5lhp/2015.WildmanEtAl.EmergingPysch.Rbb.pdf?dl=0}{PDF} \href{https://www.dropbox.com/s/or9ty6xkr8zsy0r/tandf_rrbb205_89.bib?dl=0}{BIB}



\subsubsection*{2014} 



\bibitem{Botero:2014aa}
\textcolor{Orange}{Botero, C.~A., Gardner, B., Kirby, K.~R., {\bf Bulbulia, J.}, Gavin, M.~C., \& Gray,
  R.~D. (2014).
\newblock The ecology of religious beliefs.
\newblock {\em Proceedings of the National Academy of Sciences},
  111(47), 16784--16789. }
\href{http://www.pnas.org/content/early/2014/11/05/1408701111.abstract?sid=852fbd5d-6be1-4888-8126-1e4ef7c787bd}{PDF} \href{https://www.dropbox.com/s/4kmuja16tvei26q/2014.boteroEtAl.bib?dl=0}{BIB}


\bibitem{Bulbulia:2014aa}
{\bf Bulbulia, J.}, Wilson, M.~S., \& Sibley, C.~G. (2014).
\newblock Thin and thinner: Hypothesis-driven research and the study of humans.
\newblock {\em Numen}, 61(2-3), 166--181. 
\href{https://www.dropbox.com/s/7gj657l635ap143/NU_061_02-03_166-181.pdf?dl=0}{PDF} 
\href{https://www.dropbox.com/s/p8t8m02g13fbubu/15685276-12341314.bib?dl=0}{BIB}


\bibitem{Bulbulia:2014oq}
\textcolor{Purple}{
{\bf Bulbulia, J.} (2014).
\newblock The arts transform the cognitive science of religion.
\newblock {\em Journal for the Cognitive Science of Religion}, 1(2), 141--160.}
\newblock \href{https://www.dropbox.com/s/gbz16yryorq7egu/pdfgt3Nzf.pdf}{PDF} 
\href{https://www.dropbox.com/s/3l1bebxg4cln7q0/2014.BulbuliaArts.bib?dl=0}{BIB}

% 52
\bibitem{Bulbulia:2014ab}
{\bf Bulbulia, J.} (2014).
\newblock Review: Changing minds: Religion and cognition through the ages.
\newblock {\em Journal for the Cognitive Science of Religion}, 2(1), 75--78. 
\href{https://www.dropbox.com/s/8sttr3tn8j4zwo5/2014.bulbulia.article.review.Czachesz.Biro.pdf?dl=0}{PDF}


\bibitem{Fischer:2014aa}
Fischer, R., Xygalatas, D., Mitkidis, P., Reddish, P., Tok, P., Konvalinka, I.,
  \& {\bf Bulbulia, J.}. (2014).
\newblock The fire-walker's high: Affect and physiological responses in an
  extreme collective ritual.
\newblock {\em PLoS ONE}, 9(2), e88355. 
%\href{http://www.plosone.org/article/citationList.action?articleURI=info%3Adoi%2F10.1371%2Fjournal.pone.0088355}{PDF} \href{https://www.dropbox.com/s/35bwxeutxyxwnbj/info%253Adoi%252F10.1371%252Fjournal.pone.0088355.bib}{BIB}


\bibitem{Milojev:2014aa}
Milojev, P., Osborne, D., Greaves, L., {\bf Bulbulia, J.}, Wilson, M.~S., Davies, C., Liu, J., \& Sibley, C.~G. (2014).
\newblock Right-wing authoritarianism and social dominance orientation predict
  different moral signatures.
\newblock {\em Social Justice Research}, 27(2), 149--174. 
%\href{https://www.dropbox.com/s/6yzbwpft6txa3e1/Milojev%20et%20al%20%28in%20press%29%20SJR%20Moral%20Signatures.pdf?dl=0}{PDF} \href{https://www.dropbox.com/s/u3pqsmu7rpk5h04/10.1007%252Fs11211-014-0213-7-2.bib?dl=0}{BIB}


\bibitem{Reddish:2014aa}
Reddish, P., {\bf Bulbulia, J.}, \& Fischer, R. (2014).
\newblock Does synchrony promote generalized prosociality?
\newblock {\em Religion, Brain \& Behavior}, 4(1), 3--19. 
%\href{https://www.dropbox.com/s/7811smmlz0dwh3a/ReddishSynchrony_PUBLISHED_2153599x%252E2013%252E764545.pdf}{PDF} \href{https://www.dropbox.com/s/83wv51glxm7md9r/2014.SynchGeneral.bib?dl=0}{BIB}


\bibitem{Sibley:2014aa}
\textcolor{Orange}{Sibley, C.~G., \& {\bf Bulbulia, J.} (2014). 
\newblock How do religious identities and basic value orientations affect each
  other over time?
\newblock {\em International Journal for the Psychology of Religion},
  24(1), 64--76. 
\href{https://doi.org/10.1080/10508619.2013.771600}{DOI: 10.1080/10508619.2013.771600}}
\href{https://www.dropbox.com/s/h7gqktxwjc5z11p/10508619.2013.pdf}{PDF} 
\href{https://www.dropbox.com/s/9blm1acufkd2jrv/tandf_hjpr2024_64.bib}{BIB}


\bibitem{Troughton:2014}
Troughton, G., {\bf Bulbulia, J.}, \& Sibley, C.~G. (2014).
\newblock Strength of religion and the future of the churches.
\newblock {\em Stimulus: The New Zealand Journal of Christian Thought and Practice}, 21(2), 26.
%\href{https://www.dropbox.com/s/vtkfr9toczn31s1/Stimulus%20Vol%2021%20Is%202_Troughton_Bulbulia_Sibley.pdf?dl=0}{PDF} \href{https://www.dropbox.com/s/kizniqa6y4n3te0/2014.Trought.Strength.bib?dl=0}{BIB}


\bibitem{Wilson:2014aa}
Wilson, M.~S., {\bf Bulbulia, J.}, \& Sibley, C.~G. (2014).
\newblock Differences and similarities in religious and paranormal beliefs: a
  typology of distinct faith signatures.
\newblock {\em Religion, Brain \& Behavior}, 4(2), 104--126. 
%\href{https://www.dropbox.com/s/1s4tlub7z7s485u/2153599x%252E2013%252E779934.pdf?dl=0}{PDF} \href{https://www.dropbox.com/s/bjkbwycwsqj0tdi/tandf_rrbb204_104.bib?dl=0}{BIB}



\subsubsection*{2013} 



\bibitem{Bulbulia:2013}
{\bf Bulbulia, J.}, Osborne, D., \& Sibley, C.~G. (2013).
\newblock Moral foundations predict religious orientations in {N}ew {Z}ealand.
\newblock {\em PLoS ONE}, 8(12), e80224.  
%\href{http://www.plosone.org/article/info%3Adoi%2F10.1371%2Fjournal.pone.0080224}{Open Access} \href{https://www.dropbox.com/s/07ccqrmy5j84g96/10.1371%252Fjournal.pone.0080224-2.bib}{BIB}


\bibitem{Bulbulia:2013ac}
\textcolor{Orange}{{\bf Bulbulia, J.}, Xygalatas, D., Schjoedt, U., Fondevila, S., Sibley, C.~G., \& 
  Konvalinka, I. (2013).
\newblock Images from a jointly-arousing collective ritual reveal affective
  polarization.
\newblock {\em Frontiers in Psychology}, 4(960). }
\href{http://www.frontiersin.org/evolutionary_psychology_and_neuroscience/10.3389/fpsyg.2013.00960/abstract}{Open Access}   
%\href{https://www.dropbox.com/s/9c83qghal5bobti/67850_Bulbulia_Images%20From%20a%20Jointly-Arousing%20Collective%20Ritual%20Reveal%20Affective%20Polarization.bib}{BIB}


\bibitem{Bulbulia:2013ad}																															
\textcolor{Purple}{{\bf Bulbulia, J.}, Geertz, A., Atkinson, Q.~D., Cohen, E., Evans, N., Francois, P.,								
  Gintis, H., Gray, R., Henrich, J., Jordon, F., Norenzayan, A., Richerson,																
  P.~J., Slingerland, E., Turchin, P., Whitehouse, H., Widlok, T., \& Wilson,														
  D. (2013).
\newblock The cultural evolution of religion.
\newblock In P.~J. Richerson and M. Christiansen (Eds.), {\em Cultural
  Evolution} (pp. 381--404). MIT press, Cambridge, MA. \newblock [distribution for private use by permission of the \href{http://www.esforum.de}{Ernst Strungmann Forum} and \href{https://mitpress.mit.edu/books/cultural-evolution}{MIT Press}]: }\newblock %\href{https://www.dropbox.com/s/iycggz15nr91r9n/SFR12_20%20Bulbulia%20et%20al_Author%20Copy.pdf}{PDF}   \href{https://www.dropbox.com/s/g3jw8iz2x3qo5e0/jbetal_CEVOREL.bib}{BIB} 


\bibitem{Bulbulia:2010fk}
{\bf Bulbulia, J.} (2013).
\newblock Toward an evolutionary cognitive science of mental cultures: lessons
  from {F}reud.
\newblock In D. Xygalatas and W. McCorkle (Eds.), {\em Mental Culture:
  Towards a Cognitive Science of Religion} (pp. 110--127). Equinox,
  London.  
  \newblock  %\href{https://www.dropbox.com/s/j4yowmtnqlkh8qt/ACU-Mental%20Culture-PROOF1-08-Bulbulia%20copy.pdf?dl=0}{PDF}

 
\bibitem{Bulbulia:2013a}
{\bf Bulbulia, J.}, Atkinson, Q.~D., Gray, R., \& Greenhill, S. (2013).
\newblock Why do religious cultures evolve slowly? The cultural evolution of cooperative calling and the historical study of religions. In I. Czachesz and R. Uro (Eds.), {\em Mind, Morality and Magic: Cognitive Science Approaches in Biblical Studies} (pp. 197--212).
\newblock Acumen Publishing, Durham, UK.
\href{https://www.dropbox.com/s/jcf4k7e7mex62ax/2013.BulEtAl.why_rel_evo_slow.pdf?dl=0}{PDF} \href{https://www.dropbox.com/s/vva6osofhrjsd5r/2014.BulEtAl_WhyRelCultSlow.bib?dl=0}{BIB}


\bibitem{Bulbulia:2011kx}
{\bf Bulbulia, J.} (2013).
\newblock Why costly-signalling models of religion require cognitive
  psychology.
\newblock In A.~Geertz (Ed.), {\em Origins of Religion, Cognition, and
  Culture} (pp. 71--81). Equinox, London. %\href{https://www.dropbox.com/s/0nanocrstu2cdvd/Geertz%20first%20proof%2014-08-13%20chapter%202.pdf}{PDF} \href{https://www.dropbox.com/s/8nc3e0cvpxurm3l/2013.Bulbulia.whyslowly.bib?dl=0}{BIB}


\bibitem{Bulbulia:2013b}
{\bf Bulbulia, J.}, Atkinson, Q. D., Greenhill, S., \& Gray, R. (2013).
\newblock First shots fired for the phylogenetic revolution in religious
  studies.
\newblock {\em Cliodynamics: The Journal of Theoretical and Mathematical
  History}, 4(1):128--133.
\href{http://escholarship.org/uc/item/05n4z9w8#page-27}{PDF} \href{https://www.dropbox.com/s/hyj3r479lot4u54/2013.Bulbulia.First.Shots..bib?dl=0}{BIB}


\bibitem{Bulbulia:2013qy}
\textcolor{Green}{
{\bf Bulbulia, J.} (2013).
\newblock Bayes and the evolution of religious belief.
\newblock In Moreland, J.~P., Sweis, K.~A., and V., M.~C., (Eds.), {\em
  Debating Christian Theism}, (pp. 223--241). Oxford University
  Press. } \href{https://www.dropbox.com/s/4r51rkx6hs45xv5/Bayes_Bulbulia.pdf}{PDF} \href{https://www.dropbox.com/s/bvynsi68no2bywu/2013.bulbulia.bayes.bib?dl=0}{BIB}
%\href{http://global.oup.com/academic/product/debating-christian-theism-9780199755431?cc=nz&lang=en}{to book}


\bibitem{Fischer:2013fk}
Fischer, R., Callander, R., Reddish, P., \& {\bf Bulbulia, J.} (2013).
\newblock How do rituals affect cooperation?
\newblock {\em Human Nature}, 24(2):115--125.
\href{https://www.dropbox.com/s/isz3hm6j46x15jv/10.1007_s12110-013-9167-y.pdf}{PDF} %\href{https://www.dropbox.com/s/rs1chyl87faffz9/10.1007%252Fs12110-013-9167-y.bib?dl=0}{BIB}


\bibitem{hoverd2013does}
Hoverd, W.~J., {\bf Bulbulia, J.}, \& Sibley, C.~G. (2013).
\newblock Does poverty predict religion?
\newblock {\em Religion, Brain \& Behavior}, 3(3):185--200. \href{https://www.dropbox.com/s/vfc656k50e30u1c/pov_published.pdf}{PDF} \href{https://www.dropbox.com/s/sqjldzyphdvxi6q/2013.pov.bib?dl=0}{BIB}


\bibitem{Reddish:2013aa}
\textcolor{Orange}{Reddish, P., Fischer, R., \& {\bf Bulbulia, J.} (2013).
\newblock Let's dance together: Synchrony, shared intentionality and
  cooperation.
\newblock {\em PLoS ONE}, 8(8):e71182.} 
\href{https://www.dropbox.com/s/qhcenknup2xtetx/journal.pone.0071182.pdf}{PDF} %\href{http://www.plosone.org/article/info%3Adoi%2F10.1371%2Fjournal.pone.0071182}{BIB} %href{http://www.plosone.org/article/info%3Adoi%2F10.1371%2Fjournal.pone.0071182}{RIS}


\bibitem{Sibley:2013aa}
Sibley, C.~G., \& {\bf Bulbulia, J.} (2013).
\newblock The proportion of religious residents predicts the values of
  nonreligious neighbors: evidence from a national sample.
\newblock {\em Religion, Brain and Behavior}, 3(3):219--232.
\href{https://doi.org/10.1080/2153599X.2012.739740}{DOI: 10.1080/2153599X.2012.739740}
%\href{https://www.dropbox.com/s/0exhqk26e7esbhq/2153599x%252E2012%252E739740.pdf}{PDF} 
 %\href{https://www.dropbox.com/s/0exhqk26e7esbhq/2153599x%252E2012%252E739740.pdf}{BIB}


\bibitem{Schjoedt:2013aa}
Schjoedt, U., S{\o}rensen, J., Nielbo, K.~L., Xygalatas, D., Mitkidis, P., \&
  {\bf Bulbulia, J.} (2013).
\newblock Cognitive resource depletion in religious interactions.
\newblock {\em Religion, Brain \& Behavior}, 3(1):39--55. 
%\href{https://www.dropbox.com/s/00bifhnxk68wj4i/2153599x%252E2012%252E736714.pdf?dl=0}{PDF} \href{https://www.dropbox.com/s/4qa0khevjckloor/2013.Schjoedt.Cog.Deplet.bib?dl=0}{BIB}


\bibitem{Schjoedt:2013ab}
Schjoedt, U., S{\o}rensen, J., Nielbo, K.~L., Xygalatas, D., Mitkidis, P., \&
  {\bf Bulbulia, J.} (2013).
\newblock The resource model and the principle of predictive coding: a
  framework for analyzing proximate effects of ritual.
\newblock {\em Religion, Brain \& Behavior}, 3(1):79--86.
\href{https://www.dropbox.com/s/sqmgtkag4zbu3nc/schjoedtetall2013Framework.pdf?dl=0}{PDF} \href{https://scholar.google.co.nz/scholar.bib?q=info:DB2umFzhr70J:scholar.google.com/&output=citation&scisig=AAGBfm0AAAAAVTM86rinZ5ScIM9di3Db8hA7UdmttQQN&scisf=4&hl=en}{BIB}


\bibitem{Xygalatas:2013aa}
Xygalatas, D., Schjoedt, U., {\bf Bulbulia, J.}, Konvalinka, I., Jegind{\o}, E.-M.,
  Reddish, P., Geertz, A., \& Roepstoff, A. (2013).
\newblock Autobiographical memory in a fire-walking ritual.
\newblock {\em Journal of Cognition and Culture}, 13(1-2):1--16. 
\href{https://doi.org/10.1163/15685373-12342081}{DOI: 10.1163/15685373-12342081}
\href{https://www.dropbox.com/s/3srdqka56fe7av3/JOCC_Xygalatas_et_al_2013.pdf}{PDF} \href{https://www.dropbox.com/s/yc0vqndj8w8hn05/2013.xygalat.memory.bib?dl=0}{BIB}


\bibitem{xygalatas2013extreme}
\textcolor{Orange}{Xygalatas, D., Mitkidis, P., Fischer, R., Reddish, P., Skewes, J., Geertz,
  A., Roepstorff, A., \& {\bf Bulbulia, J.} (2013).
\newblock Extreme rituals promote prosociality.
\newblock {\em Psychological science}, 24(8):1602--1605.} %\href{https://www.dropbox.com/s/0d5lglhhx5gqzop/Psychological%20Science-2013-Xygalatas-0956797612472910.pdf}{PDF} \href{https://www.dropbox.com/s/axtkifeonok70yb/2013.Extreme.Xygal.bib?dl=0}{BIB}

\subsubsection*{2012} 

\bibitem{Bulbulia:2012ab}
\textcolor{Green}{{\bf Bulbulia, J.} (2012).
\newblock Spreading order: religion, cooperative niche construction, and risky
  coordination problems.
\newblock {\em Biology \& philosophy}, 27(1):1--27.}
\href{https://doi.org/10.1007/s10539-011-9295-x}{DOI: 10.1007/s10539-011-9295-x}
\href{http://www.springerlink.com/content/e4208k071t6164k7/}{Open Access} %\href{https://www.dropbox.com/s/k7pmdrr80tqwp6k/BULBULIA_10.1007_s10539-011-9295-x%20.pdf?dl=0}{PDF} \href{https://www.dropbox.com/s/io81gsw2gt1w4mk/2012.Bulbulia.SpreadOrder.bib?dl=0}{BIB}


\bibitem{Bulbulia:2012fj}
\textcolor{Green}{{\bf Bulbulia, J.} (2012).
\newblock Ennuitheism.
\newblock In P. MacNamara and W.~J. Wildman (Eds.), {\em Science and the
  World's Religions: Vol 3. Religions and Controversies} (pp. 165--194). Praeger, Santa Barbara, CA.} \href{https://www.dropbox.com/s/wgm2tsi4safdmc3/2012_Ennuitheism-bulbulia_published.pdf?dl=0}{PDF} \href{https://www.dropbox.com/s/aalocq092iqrw01/2012.Bulbulia.Ennuitheism.bib?dl=0}{BIB}


\bibitem{Bulbulia:2012aa}
{\bf Bulbulia, J.}, Frean, M., \& Reddish, P. (2012).
\newblock Ecological signalling.
\newblock In G.~W. Dawes and J. Maclaurin (Eds.), {\em A New Science of
  Religions} (pp. 100--110). Routledge. %\href{https://www.dropbox.com/s/6kvlr459l2dfzd5/BUL_Chap4-Ecol%20Sign-PROOF.pdf?dl=0}{PDF} \href{https://www.dropbox.com/s/146j28fyr5p5b6q/2012.ecological.signal.bulbuliaEtAl.bib?dl=0}{BIB}


\bibitem{Bulbulia:2012uq}
{\bf Bulbulia, J.}, \& Reddish, P. (2012).
\newblock Explaining effervescence.
\newblock In G.~W. Dawes, and J. Maclaurin (Eds.), {\em A New Science of Religions}
  (pp. 43--64). Routledge, New York. \href{https://www.dropbox.com/s/t67m0qyptuec2ix/BUL_Chap6-ExplEffe-PROOF.pdf?dl=0}{PDF} \href{https://www.dropbox.com/s/23rouucf6vs7igi/2012.explainEfferv.bul.bib?dl=0}{BIB}


\bibitem{Bulbulia:2009lb}\textcolor{Purple}{
{\bf Bulbulia, J.}, \& Schjoedt, U. (2012).
\newblock The neural basis of religious belief.
\newblock In F. Krueger and J. Grafman (Eds.), {\em The Neural Basis of
  Human Belief Systems} (pp. 169--190). Psychology Press. }\href{https://www.dropbox.com/s/lsatbexn9jasbfh/NB09.pdf?dl=0}{PDF} \href{https://www.dropbox.com/s/m4jmcqzi9i3dmj8/2013.Bulbulia.Schoedt.Neural.Belief.bib?dl=0}{BIB}


\bibitem{Bulbulia:2012kx}
{\bf Bulbulia, J.}, \& Schjoedt, U. (2012).
\newblock Toward an evolutionary social neuroscience of religion.
\newblock {\em Religion, Brain \& Behavior}, 1(3):220--222. \href{https://www.dropbox.com/s/v59etaychbt2z25/2012.bulbulia.schoedt.towardsevoneuroscince.pdf?dl=0}{PDF}


\bibitem{Bulbulia:2012ac}\textcolor{Purple}{
{\bf Bulbulia, J.}, \& Slingerland, E. (2012).
\newblock Religious studies as a life science.
\newblock {\em Numen}, 59(5-6):564--613.} \href{https://www.dropbox.com/s/eom9r3jbt1qvg4a/NU_059_05-06_564-613.pdf}{PDF} \href{https://www.dropbox.com/s/y8o9w2bvnwjimxk/2012.Bulbulia.Slingerland.Ritual.bib?dl=0}{BIB}


\bibitem{Sibley:2012fk}
Sibley, C.~G., \& {\bf Bulbulia, J.} (2012).
\newblock Healing those who need healing: How religious practice interacts with
  personality to affect social belonging.
\newblock {\em Journal for The Cognitive Science of Religion}, 1(1):29--45. \href{https://www.equinoxpub.com/journals/index.php/JCSR/article/viewArticle/Healing-Those-Who-Need-Healing}{PDF} \href{https://www.dropbox.com/s/nbd18kv59i1s98a/healing.those.bib?dl=0}{BIB}


\bibitem{Schjoedt:2012kx}
Schjoedt, U., \& {\bf Bulbulia, J.} (2012).
\newblock The need to believe in conflicting propositions.
\newblock {\em Religion, Brain \& Behavior}, 1(3):236--239.
\href{http://www.tandfonline.com/doi/abs/10.1080/2153599X.2011.647857}{PDF} \href{https://www.dropbox.com/s/trju867snuho33k/needtobelieve.bib?dl=0}{BIB}


\bibitem{sibley2012faith}
\textcolor{Orange}{Sibley, C.~G., \& {\bf Bulbulia, J.} (2012).
\newblock Faith after an earthquake: A longitudinal study of religion and
  perceived health before and after the 2011 {C}hristchurch {N}ew {Z}ealand
  earthquake.
\newblock {\em PLoS one}, 7(12):e49648.\newblock 
\href{https://doi.org/10.1371/journal.pone.0049648}{DOI: 10.1371/journal.pone.0049648}}
%\newblock \href{http://www.plosone.org/article/info%3Adoi%2F10.1371%2Fjournal.pone.0049648}{Open Access PDF + Slides} \href{https://www.dropbox.com/s/p02sexw53slcpn6/faithquake.bib?dl=0}{BIB}



\subsubsection*{2011} 



\bibitem{Bulbulia:2011aa}
{\bf Bulbulia, J.}, \& Frean, M. (2011).
\newblock Affording cooperative populations.
\newblock {\em Religion, Brain \& Behavior}, 1(1):66--70. \href{https://www.dropbox.com/s/2zksrbyav9agt14/BULBULIA_AFFORDING_2011.pdf?dl=0}{PDF} \href{https://www.dropbox.com/s/nkk7yepibk3f696/tandf_rrbb201_66.bib?dl=0}{BIB}


\bibitem{Bulbulia:2011ab}\textcolor{Purple}{
{\bf Bulbulia, J.}, \& Sosis, R. (2011).
\newblock Signalling theory and the evolution of religious cooperation.
\newblock {\em Religion}, 41(3):363--388. 
\href{https://doi.org/10.1080/0048721X.2011.604508}{DOI: 10.1080/0048721X.2011.604508}}
\newblock \href{https://www.dropbox.com/s/j0zb0a74ut3j93r/Bulbulia_Sosis_Signalling_2011.pdf}{PDF} \href{https://www.dropbox.com/s/yxcfyzqa8d342em/sig.theory.bul.sos.bib?dl=0}{BIB}


\bibitem{Bulbulia:2011ac}
{\bf Bulbulia, J.} (2011).
\newblock The hypnotic stag hunt.
\newblock {\em Journal of Cognition and Culture}, 11(3-4):353--365. 
\href{https://doi.org/10.1163/156853711X591297}{DOI: 10.1163/156853711X591297}
 \href{https://www.dropbox.com/s/ngdi2ldwnny7sd8/JOCC_011_03-04_06-Bulbulia.pdf}{PDF} \href{https://www.dropbox.com/s/o5lkyk8uvsuytn1/Hypnotic.bib?dl=0}{BIB}


\bibitem{Bulbulia:2011ad}
Frean, M., \& {\bf Bulbulia, J.} (2011).
\newblock Neutral evolution as a route to large-scale cooperation in the stag
  hunt game.
\newblock In {\em International Conference on Complex Systems (ICCS) 2011,
  hosted by NECSI (New England Complex Systems Institute July 1-6, 2011
  (proceedings)}.
%\href{http://homepages.ecs.vuw.ac.nz/foswiki/pub/Users/Marcus/MarcusFreanPublications/ICCS-259-FreanBulbulia.pdf}{LINK}. 
  \href{https://www.dropbox.com/s/bn4p7ry1cwz2v76/ICCS-259-FreanBulbulia.pdf?dl=0}{PDF}
 

\bibitem{Konvalinka:2010zr}
\textcolor{Orange}{Konvalinka, I., Xygalatas, D., {\bf Bulbulia, J.}, Schjoedt, U., Jegindoe, E.~M.,
  Wallot, S., Van~Orden, G., \& Roepstorff, A. (2011).
\newblock Synchronized arousal between performers and related spectators in a
  fire-walking ritual.
\newblock {\em Proceedings of the National Academy of Sciences},
  108(20):8514--8519.}  \href{https://www.dropbox.com/s/e9kw1bc58arqcum/1016955108-1.full.pdf}{PDF} \href{https://scholar.google.co.nz/scholar.bib?q=info:Z4bz7lwp7CAJ:scholar.google.com/&output=citation&scisig=AAGBfm0AAAAAVQLQj1q3zL48FKlyJACORNS7cgksQjIL&scisf=4&hl=en}{BIB}


\bibitem{Slingerland:2011aa}
Slingerland, E., \& {\bf Bulbulia, J.} (2011).
\newblock Introductory essay: Evolutionary science and the study of religion.
\newblock {\em Religion}, 41(3):307--328. 
\href{https://doi.org/10.1080/0048721X.2011.604513 }{DOI: 10.1080/0048721X.2011.604513}
	\newblock \href{https://www.dropbox.com/s/w7om74yu1byjces/Slingerland_Bulbulia_2011.pdf?dl=0}{PDF} \href{https://scholar.google.co.nz/scholar.bib?q=info:EuqNIKJICaAJ:scholar.google.com/&output=citation&scisig=AAGBfm0AAAAAVQLQF9j3ZcOMiq4s0i0IlD2LvlZZY93D&scisf=4&hl=en}{BIB}


\bibitem{Sosis:2011uq}
Sosis, R., \& {\bf Bulbulia, J.} (2011).
\newblock The behavioral ecology of religion: the benefits and costs of one
  evolutionary approach.
\newblock {\em Religion}, 41(3):341--362. 
\href{https://doi.org/10.1080/0048721X.2011.604514}{DOI: 10.1080/0048721X.2011.604514} \newblock \href{https://www.dropbox.com/s/x6qyj01trcuhfzd/SosisBulbuliaBehEcoRel.pdf?dl=0}{PDF} \href{https://scholar.google.co.nz/scholar.bib?q=info:6KFNe9NrUB0J:scholar.google.com/&output=citation&scisig=AAGBfm0AAAAAVQLQzUevx-JM_Jt5ZX4k_9fxb6dV3u0s&scisf=4&hl=en}{BIB}\


\bibitem{Xygalatas:2011ij}
Xygalatas, D., Konvalinka, I., Roepstoff, A., \& {\bf Bulbulia, J.} (2011).
\newblock Quantifying collective effervescence heart-rate dynamics at a
  fire-walking ritual.
\newblock {\em Communicative and Integrative Biology}, 4(6):735--738.\newblock 
\href{https://doi.org/10.4161/cib.4.6.17609}{DOI: 10.4161/cib.4.6.17609}
\href{https://www.dropbox.com/s/k7sd19xlfiq8huo/XygalatasCIB4-6.pdf}{PDF} \href{https://scholar.google.co.nz/scholar.bib?q=info:ibIMcXjOt4sJ:scholar.google.com/&output=citation&scisig=AAGBfm0AAAAAVQLRpR7fjyHaIZem3vp4nLctXQZrVMcE&scisf=4&hl=en}{BIB} 



\subsubsection*{2010}



\bibitem{Bulbulia:2010fv}
{\bf Bulbulia, J.}, \& Frean, M. (2010).
\newblock The evolution of charismatic cultures.
\newblock {\em Method and Theory in the Study of Religion}, 22(4):254--271. 
\href{https://doi.org/10.1163/157006810X531049}{DOI: 10.1163/157006810X531049}  \href{http://db.tt/3EhwMDv}{PDF} \href{https://scholar.google.co.nz/scholar.bib?q=info:CMgUm8a7Y_QJ:scholar.google.com/&output=citation&scisig=AAGBfm0AAAAAVQPQTOqB9pbHY7FLyLOV1miSoIIZ5shl&scisf=4&hl=en}{BIB}


\bibitem{Bulbulia:vn}
{\bf Bulbulia, J.}, \& Schjoedt, U. (2010).
\newblock Religious Culture and Cooperative Prediction under Risk: Perspectives from Social Neuroscience.
\newblock In I. Pyysiainen (Ed.), {\em Religion, Economy, and Cooperation},
 (pp. 35--59). deGruyter, New York. \href{http://db.tt/MOZlvjr}{PDF}


\subsubsection*{2009}



\bibitem{Bulbulia:2009iw}\textcolor{Green}{
{\bf Bulbulia, J.} (2009).
\newblock Charismatic signalling.
\newblock {\em Journal for the Study of Religion, Nature, Culture},
  3(4):518--551.} \newblock 
\href{https://doi.org/10.1558/jsrnc.v3i4.518}{DOI: 10.1558/jsrnc.v3i4.518} \newblock \href{http://db.tt/8IiltRr}{PDF} \href{https://scholar.google.co.nz/scholar.bib?q=info:eUGNRtbVR88J:scholar.google.com/&output=citation&scisig=AAGBfm0AAAAAVQPSkHpPrfY5B1nrjrJcYvQiHbdtIIuQ&scisf=4&hl=en}{BIB}


\bibitem{Bulbulia:2009qg}
{\bf Bulbulia, J.} \& Krueger, F. (2009). Comment on Attachment and Cooperation in Religious Groups.
\newblock 
\newblock{\em Current Anthropology}, 50(6):772--773.
\href{https://doi.org/10.1086/605767}{DOI: 10.1086/605767} \newblock \href{http://db.tt/MMaLhwQ}{PDF}


\bibitem{Bulbulia:2009fk}
{\bf Bulbulia, J.} \& Sosis, R. (2009).
\newblock Belief as ideology.
\newblock {\em Behavior and the Brain Sciences}, 32(6):515--516. 
\href{https://doi.org/10.1017/S0140525X09991403}{DOI: 10.1017/S0140525X09991403} \newblock \href{http://db.tt/I9z2SCY}{PDF}


\bibitem{Bulbulia:2009aa} 
{\bf Bulbulia, J.} (2009).
\newblock Religion as evolutionary cascade.
\newblock In M. Stuasberg (Ed.), {\em Contemporary Theories of Religion: A
  Critical Companion} (pp. 156--172). Routledge, New York. \href{http://db.tt/OLFGqFk}{PDF}


\bibitem{Bulbulia:2009fv}
{\bf Bulbulia, J.}, \& Frean, M. (2009).
\newblock Religion as superorganism.
\newblock In M. Stausberg (Ed.), {\em Contemporary Theories of Religion: A
  Critical Companion} (pp. 173--194). Routledge, New York. \href{http://db.tt/LMShwLD}{PDF}


\bibitem{Bulbulia:2009vv}
\textcolor{Green}{{\bf Bulbulia, J.} (2009).
\newblock Religiosity as mental time travel: cognitive adaptations for
  religious behavior.
\newblock In J. Schloss and M. Murray (Eds.), {\em The Believing Primate:
  Scientific, Philosophical and Theological Perspectives on the Evolution of
  Religion} (pp. 44--75). Oxford University Press, New York. } \href{http://db.tt/gGUysok}{PDF} \href{https://www.dropbox.com/s/ri6hs7gbut6ku1f/2009.mentalTime.bib?dl=0}{BIB}



\subsubsection*{2008}




\bibitem{Bulbulia:2008bu}
 \textcolor{Green}{{\bf Bulbulia, J.} (2008).
\newblock Meme infection or religious niche construction? an adaptationist
  alternative to the cultural maladaptationist hypothesis.
\newblock {\em Method and Theory in the Study of Religion}, 20(1):67--107.} \href{http://db.tt/6IjKsQV}{PDF} \href{https://scholar.google.co.nz/scholar.bib?q=info:7ZPnl0WG0EkJ:scholar.google.com/&output=citation&scisig=AAGBfm0AAAAAVQSUw7EcGrYvW0TZ0foofELIVjbg3S2W&scisf=4&hl=en}{BIB}


\bibitem{Bulbulia:2008fp}
{\bf Bulbulia, J.} (2008).
\newblock Ritual studies and ritual theories: A guide for the perplexed.
\newblock {\em Numen}, 55(4):461--473.  
\href{https://doi.org/1163/156852708X310545}{DOI: 1163/156852708X310545} \href{http://booksandjournals.brillonline.com/content/journals/10.1163/156852708x310545}{PDF}


\bibitem{Bulbulia:2008ly}
{\bf Bulbulia, J.} (2008).
\newblock Telling nature.
\newblock {\em Landfall}, 215:180--185.\href{http://db.tt/MCbgvBt}{PDF}


\bibitem{Bulbulia:2008lf}\textcolor{Green}{
{\bf Bulbulia, J.} (2008).
\newblock Free love: Religious solidarity on the cheap.
\newblock In J. Bulbulia, R. Sosis, R. Genet, R, E. Harris, K. Wyman and
  C. Genet (Eds.), {\em The Evolution of Religion: Studies, Theories, and
  Critiques}, (pp. 153--160). Collins Foundation Press, Santa
  Margarita, CA.} \href{http://db.tt/8vbZ8wQ}{PDF}  \href{https://www.dropbox.com/s/57zbcpj8llfrlgy/freeLove.bib?dl=0}{BIB}
  

\bibitem{Bulbulia:2008sk}\textcolor{Orange}{
{\bf Bulbulia, J.}, \& Mahoney, A. (2008).
\newblock Religious solidarity: The hand grenade experiment.
\newblock {\em Journal of Cognition and Culture}, 8(3):295--320.
\href{https://doi.org/10.1163/156853708X358191}{DOI: 10.1163/156853708X358191} \newblock} \href{http://db.tt/0969FhI}{PDF} \href{https://scholar.google.co.nz/scholar.bib?q=info:ez_RmJh3ov8J:scholar.google.com/&output=citation&scisig=AAGBfm0AAAAAVQSZK_McRldG-i1APaLH3OkcaGDXrgxr&scisf=4&hl=en}{BIB}


\bibitem{Sosis:2007yd}
Sosis, R., \& {\bf Bulbulia, J.} (2008).
\newblock Religion in Eden.
\newblock In J. Bulbulia, R. Sosis, R. Genet, E. Harris, K. Wyman and
  C. Genet (Eds.), {\em The Evolution of Religion: Studies, Theories, and
  Critiques}, Chapter Introduction (pp. 15--19). Collins Foundation Press,
  Santa Margarita, CA. \href{http://db.tt/nSs5qqb}{PDF}



\subsubsection*{2007}



\bibitem{Bulbulia:2007vo}\textcolor{Purple}{
{\bf Bulbulia, J.} (2007).
\newblock The evolution of religion.
\newblock In R. Dunbar and L. Barrett (Eds.), {\em Oxford Handbook of
  Evolutionary Psychology} (pp. 621--636). Oxford University
  Press, New York.} \href{http://db.tt/nSs5qqb}{PDF} \href{https://www.dropbox.com/s/owcmsyw09umhc1x/theEvoReligion.bib?dl=0}{BIB}


\subsubsection*{2006}
\bibitem{Bulbulia:2006iu}\textcolor{Green}{
{\bf Bulbulia, J.} (2006).
\newblock Nature's medicine: religiosity as an adaptation for health and
  cooperation.
\newblock In P. McNamara (Ed.), {\em Where Man and God Meet: the new
  sciences of religion and brain}, (pp.~87--121). Greenwood
  Publishers, Westwood CT.} \href{http://db.tt/HFNrN38}{PDF}



\subsubsection*{pre-2005}



\bibitem{Bulbulia:2005jl}\textcolor{Green}{
{\bf Bulbulia, J.} (2005).
\newblock Are there any religions?
\newblock {\em Method and Theory in the Study of Religion}, 17(2):71--100. 
\href{https://doi.org/10.1163/1570068054305619}{DOI: 10.1163/1570068054305619}} \href{http://db.tt/IUco0fj}{PDF} \href{https://scholar.google.co.nz/scholar.bib?q=info:VkW9oOZSmf8J:scholar.google.com/&output=citation&scisig=AAGBfm0AAAAAVQSb1HVG338RqWQkIIV6dbi-5mWgu0GN&scisf=4&hl=en}{BIB}


\bibitem{Bulbulia:2004yo} \textcolor{Green}{
{\bf Bulbulia, J.} (2004).
\newblock Religious costs as adaptations that signal altruistic intention.
\newblock {\em Evolution and Cognition}, 10(1):19--38.}   \href{http://db.tt/BCahAsL}{PDF} \href{https://scholar.google.co.nz/scholar.bib?q=info:S_Eaz9FFNg4J:scholar.google.com/&output=citation&scisig=AAGBfm0AAAAAVQScQ3OHzAiiRCA0uahLpFkCTVIuvpok&scisf=4&hl=en}{BIB}


\bibitem{Bulbulia:2004be}
\textcolor{Purple}{{\bf Bulbulia, J.} (2004).
\newblock The cognitive and evolutionary psychology of religion.
\newblock {\em Biology and Philosophy}, 18(5):655--686.} \href{http://db.tt/QyYditX}{PDF} \href{https://scholar.google.co.nz/scholar.bib?q=info:wfjh1TV9XQsJ:scholar.google.com/&output=citation&scisig=AAGBfm0AAAAAVQSiEyp4iOATTHZI5hVnJLq3P73FdO1P&scisf=4&hl=en}{BIB}


\bibitem{Bulbulia:2003ol}
{\bf Bulbulia, J.} (2003).
\newblock Book review: Nicholas Agar, Life's Intrinsic Value: Science, Ethics and Nature.
\newblock {\em Sophia}, 42(1):85--89. \href{http://db.tt/o8XLYrL}{PDF}


\bibitem{Bulbulia:2003aa}
{\bf Bulbulia, J.} (2003).
\newblock Review of {J}ames {M}cclenon: {W}ondrous Healing: Shamanism, Human
  Evolution and the Origin of Religion.
\newblock {\em Method \& Theory in the Study of Religion}, 15(1):100--103. 
\href{https://doi.org/10.1163/15700680360549439}{DOI: 10.1163/15700680360549439} \href{http://db.tt/AO5Ut4S}{PDF}



\bibitem{Bulbulia:2002ve}
{\bf Bulbulia, J.} (2002).
\newblock Unweaving the religious mind: A review of Pascal Boyer, religion ex-
  plained: The evolutionary origins of religious thought.
\newblock {\em Eras}, 4. \href{http://www.arts.monash.edu.au/publications/eras/edition-4/bulbulia.php}{URL}


\bibitem {Bulbulia:1997aa}
{\bf Bulbulia, J.} (1996).
\newblock Book review: {H}ilary {P}utnam, {W}ords and {L}ife .
\newblock {\em Koinonia}, 8. \href{http://db.tt/vygRUWn}{(DOC)} \href{http://www.ptsem.edu/koinonia/}{Journal}



\subsubsection*{Edited Books} 



\bibitem{Bulbulia:2008jb}
{\bf Bulbulia, J.}, Sosis, R., Genet, R., Harris, E., Wyman, K., \& Genet, C.
  (2008).\newblock {\em The Evolution of Religion: Studies, Theories, and Critiques}.
\newblock Collins Foundation Press, Santa Margarita, CA. %\href{https://www.dropbox.com/s/hgbsysc1ioluay5/Evolution%20of%20Religion%2C%20Bulbulia%20et%20al.pdf?dl=0}{PDF}


\bibitem{Bulbulia:2004ld}
{\bf Bulbulia, J.}, \& Morris, P. (2004).
\newblock {\em What is Religion For?}
\newblock Milne, Wellington.


\subsubsection*{Dissertation} 
\bibitem{Bulbulia:2001cr}
{\bf Bulbulia, J.} (2001).
\newblock {\em Before Eden: Religion and The Evolved Mind}.
\newblock PhD thesis, Princeton University, Princeton, N.J.  %\href{https://www.dropbox.com/s/czvxvm24o8r5n55/Bulbulia%20diss.pdf?dl=0}{PDF}


\end{thebibliography}


\subsubsection*{Supervisions}
\subsection*{Completed}
\noindent

\years{2015$\to$2018} S. A. Teo. {\em Ph.D. Religious Studies}. Religion as a marker of communal boundaries: Revivalism and Hindu temples in Malaysia. Secondary supervisor.\\
%
\years{2015$\to$2018}R.~Mogan. {\em Ph.D. Psychology}. Aligning Bodies And Minds: New Insights And A Synthesis Of Synchronys Effects On Creative Thinking, Cohesion And Positive Affect.  Secondary supervisor.\\
%
\years{2014$\to$2017} B. A. ~Blaschke. {\em Ph.D. Religious Studies}. Contemplative Responses to the Problem of Self: An Ethnography of the Spirit. Secondary supervisor.\\
%
\years{2016} D.~Robinson. {\em M.A. Religious Studies}. Religion and Social Capital in New Zealand. Primary supervisor.\\
%
\years{2015}B.~Davis.{ \em Ph.D. Religious Studies}. Psychology, Cosmology and the Christian Concept of God: Reconciling Theology and Science. Primary supervisor\\
%
\years{2015}R.~Somerfield.{ \em Ph.D. Theatre Studies}. Moving Minds: Undoing cognition in performance environments. Secondary supervisor.\\
%
\years{2015}D.~Murphy.{ \em Ph.D. Religious Studies (scholarship)}. Maori Myth and Extended Cognition: a cognitive approach to memory and oral tradition in the Pacific. Primary supervisor.\\
%
\years{2013}P.~Reddish.{ \em Ph.D. Pyschology (scholarship)}. The Cooperative Effects of Synchronous Interactions. Secondary supervisor.\\%defended 24 OCT 2012
%
\years{2011}C.~Dalzell.{ \em M.A. Religious Studies}. Selecting for Celibacy - Cultural evolution and the puzzling case of Buddhist celibacy. Awarded with distinction. Primary supervisor.\\
%
\years{2011}T.~McVicar. {\em M.A. Religious Studies}. Implicit Cultures: Towards a Psychosocial Theory of Intuitive Religious Beliefs. Awarded with distinction. Primary supervisor.\\
%
\years{2010}A.~Mahoney. {\em Ph.D. Religious Studies (Bright Futures)}. The Evolutionary Psychology of Theology. Primary supervisor.\\
%
\years{2009}S.~Hill. {\em Ph.D. Sociology}. Torn Between Boundaries: Bodies-in-pain, Christianity and Feature Film. Secondary supervisor.\\
%
\years{2009}D.~Murphy. {\em M.A. Religious Studies}. Sacred Technologies: The evolution of the religious cognitive Niche. Awarded with distinction. Primary supervisor.\\
%
\years{2007}A.~Robertson. {\em Ph.D. Psychology}. In Search of a Theoretical Explanation for The Relationship Between Religion and Prejudice. Secondary supervisor.\\ %with Marc Wilson, Psychology.\\
%
\years{2006}Y.~Jeon. {\em Ph.D. Media Studies}. Communication Models of Adolescent Religious Education on The Internet in A Global Age.  Secondary supervisor.% with Rowen Cullen, Media Studies.


\subsubsection*{Ongoing}
\noindent
\years{2019$\to$}R. Bonifant. Transmission of Anglican Belief and Practice in Aotearoa New Zealand. Primary Supervisor. \\
\years{2015$\to$2020}K. Deak (Submitted). The religious paradox of gender inequality and well-being
an evolutionary account of parental cooperation. Secondary Supervisor.\\
%\years{2011$\to$}K.~Sterhle.{ \em Ph.D. cand. Religious Studies}. Secondary supervisor, with Rick Weiss, Religious Studies.\\
%\bibitem{CS:SS}
%C.~Ferrario.{ \em Ph.D. cand. Philosophy}
%\newblock Enroled 2010. Secondary supervisor.

% \years{2008$\to$}E.~Czarnecki.{ \em Ph.D. cand. Religious Studies}. {\em Conceptual Analysis of Costly Signaling.} Primary supervisor, with Marcus Frean, Computer Science.\\
%\years{2008$\to$}A.~Searfross.{ \em Ph.D. cand. Religious Studies}. {\em Transmission and Storage of Memory.} Secondary supervisor, with Paul %Morris, Religious Studies.

%\bibitem{Teitelbaum:2006fv}
%M.~Teitelbaum.{ \em Ph.D. cand. Religious Studies}. Enroled 2007. Primary supervisor.


\subsubsection*{Presentations} 
\subsubsection*{Keynotes \& Invited}

\years{2019$^k$} Attitudes to religion and trade in New Zealand (2009-2018). Religion and Business: Reaping the Diversity Dividend. Auckland University of Technology, Auckland, New Zealand. 12 August 2019. \href{https://www.dropbox.com/s/t0vsqu95nbs32t6/2019.AUG.12.bulbulia.Biz.Rel.pptx?dl=0}{LINK}\\
\years{2019$^t$} The interplay of religious affiliation and volunteering, evidence from The New Zealand Attitudes and Values Study 2009-2019.  Templeton Annual Meeting. Nassau, Bahamas. 24 June 2019.\\
\years{2019$^t$} What are the sources of Muslim Acceptance in New Zealand? Maclaurin Chapel, Auckland, New Zealand. May 28 2019. \\
\years{2019$^k$} Changing Attitudes to Muslims in New Zealand: years 2013-2017. Amnesty International Annual Hui 2019: IMPACT for Human Rights. Wellington, New Zealand. 10 May 2019.\\
\years{2018$^t$} How Spiritual Are We Really? Engage Conference. Auckland, New Zealand. 21 September 2018.\\
\years{2018$^k$} Teams $>$ STEM $+$ HASS. Plenary Session. International. Deans of Arts, Social Sciences and Humanities Conference (Australasia). Australian National University, Canberra, Australia. 12 September 2018.\\
\years{2018$^k$} Is Virtue Worth The Effort? International Humanist Conference. Auckland, New Zealand. 4 August 2018.\\
\years{2018$^k$} Religion and the evolution of second nature? Erice, Sicily. 12 May 2018.\\
\years{2017$^k$}Computational Phylogenetic Methods Test Functional Hypotheses About Culture. University of Helsinki. 25 May 2017. \\ 
\years{2016$^t$} {\bf J.~Bulbulia}, Presidential Address. International Association for the Cognitive Science of Religion. Vancouver, Canada. 24 August 2016.\\
\years{2012$^t$}{\bf J.~Bulbulia}, \newblock\href{http://conferences.au.dk/biologicalandculturalevolution/conference-programme/}{~Religious Ritual, Identity, and Coordination: Surprising Results From the Field}\newblock Keynote: Aarhus University, \href{http://conferences.au.dk/biologicalandculturalevolution/}{Biological and Cultural Evolution and Their Interactions}. Denmark.~26~June~2012. \\
\years{2011$^t$}{\bf J.~Bulbulia}, \newblock \href{http://db.tt/8CgWl7MC}{Experimental Anthropology: How Quantitative Field Studies are Revealing New Subtleties in Religious Rituals}
\newblock (invited talk). Aarhus University, Denmark. 18 October 2011. \href{http://aal.au.dk/antro/conference-2011-researching-religion/programme/}{{\bf Website}}\\
\years{2009$^k$}I.~Konvalinka, \textbf{J.~Bulbulia}, D. Xygalatas, and U.~Schjoedt, 
Synchronous arousal memory in a Spanish firewalk.
\newblock Keynote Address, International Association for the Cognitive Study of Religion: Cognitive Science Society Annual Meeting. Amsterdam, Netherlands. July 2009.\\
\years{2008$^k$}{\bf J.~Bulbulia}, Bayes theorem and the economics of religious reciprocity.\newblock Keynote Address, European Collaborative Research Foundation. Consciousness in Natural Context. Aarhus University, Denmark. June 2008.\\
\years{2008$^k$}{\bf J.~Bulbulia}, \href{http://video.google.com/videoplay?docid=4493321247767166938#}{The human nest: Epistemic niche construction and religiosity}.\newblock Keynote Address, Religious Ritual, Cognition and Culture. Aarhus University, Denmark. May 2008.\\
\years{2006$^k$}{\bf J.~Bulbulia}, Why religious commitment is also moral commitment.\newblock Faculty Keynote. Aarhus University, Denmark. 7 December 2006.

\subsubsection*{Talks}
\years{2020$t$} A national scale longitudinal analysis of the Social Consequences of Religion in New Zealand: 2009-2017 (Three Studies). Templeton Religion Trust. Nassau, Bahamas. 14 January 2020. \\
\years{2019$^t$} A national scale longitudinal analysis of mis/perceptions about Religious Faith and Practice in New Zealand: 2009-2017 (Three Studies). University of the 3rd Age (U3A). New Plymouth, New Zealand. 13 November 2019. \href{https://www.dropbox.com/s/xypex3ektzf51cb/Bulbulia.NewPLymoth.NOV.13.2019.pptx?dl=0}{LINK}\\
\years{2019$t$} Extremism in New Zealand reveals challenges and opportunities for international education partnerships. University of Auckland U21. University of Auckland, Auckland, New Zealand. 25 October 2019. \href{https://www.dropbox.com/s/33q0ths4o9pml9l/v4.bulbulia_Auckland_u21_OCT.25.2019.low.res.pptx?dl=0}{LINK} \\
\years{2019$t$} The interplay of religious affiliation and volunteering, evidence from the New Zealand Attitudes and Values Study 2009-2019. Templeton Religion Trust advisory meeting on the SCORE initiative. Oxford, UK. October 2019. \href{https://www.dropbox.com/s/zsggoh701jvqqnv/v4.Bulbulia.TRT_Presentation.JUNE_23.2019.pptx?dl=0}{LINK}\\
\years{2017$t$} Two paradoxes of religious change in New Zealand. \newblock NCLANZ Meeting. Wellington, New Zealand. 19 September 2017.\\
\years{2017$t$} Punctuated Evolution of Religion, Cultural Evolution Society Conference. Jena, Germany. 14 September 2017.\\
\years{2017$t$} Religion and the good life in New Zealand, 8th Christian Leaders Congress. Hope Centre, Wellington, New Zealand. 23 March 2017.\\
\years{2017$t$} Darwin meets Luther: How Evolutionary Religious Studies Explains the Protestant Reformation. \newblock  Empirical Philosophy Workshop. Wellington, New Zealand. 1 June 2017. \\
\years{2016$^t$} Secularization and Simpson's Paradox. Otago University, Dunedin, New Zealand. October 2016.\\
\years{2016$^t$} {\bf J. Bulbulia}, Sex, Signaling, \& Religion Today. International Association for the Cognitive Science of Religion. Vancouver, Canada. 24 August 2016.\\
\years{2016$^t$} {\bf J. Bulbulia}, Evolutionary Theory meets Big Longitudinal Data: Modeling Religion, Tolerance, and Prejudice in a Western Secular Society. International Association for the Cognitive Science of Religion. Vancouver, Canada. 23 August 2016.\\
\years{2016$^t$} {\bf J. Bulbulia}, Religion Evolves Social Inequality. Victoria University Religious Studies Seminar. Wellington, New Zealand. 24 March 2016.\\
\years{2016$^t$} {\bf J. Bulbulia}, Religion and the Evolution of Social Inequality. University of Otago, Psychology Department. University of Otago, Dunedin, New Zealand. 22 February 2016. \\
\years{2015$^t$} {\bf J. Bulbulia}, Longitudinal Study of Religion: recent findings from the New Zealand Attitudes \& Values Study. Queenstown. 8 December 2015.  \\
\years{2015$^t$} {\bf J. Bulbulia},  Religion and the Evolution of Social Inequality. Victoria University, Wellington, New Zealand. October 6 2015\\
\years{2015$^t$} {\bf J. Bulbulia}, Computational Phylogenetic Methods Test Functional Hypotheses About Culture. California Technical Institute, Los Angeles, USA. 2 September, 2015.\\
\years{2015$^t$} {\bf J. Bulbulia}, J. Watts, S. Greenhill, and R. Gray, The Punctuated Evolution of Religion. International Association for the History of Religions.  Erfurt, Germany. 28 Aug, 2015.\\
\years{2015$^t$} {\bf J. Bulbulia}, Recording History to Understand it: Longitudinal Study of Religion in New Zealand. International Association for the History of Religions.  Erfurt, Germany. 25 Aug, 2015.\\
\years{2015$^t$} {\bf J. Bulbulia}, Religion and Charity in New Zealand. International Association for the History of Religions. Erfurt, Germany. 25 Aug, 2015.\\
\years{2015$^t$} J. Watts, R. Gray, and {\bf J. Bulbulia}, Broad supernatural punishment but not moralising high gods precede the evolution of political complexity in Austronesia. Victoria University Empirical Philosophy Workshop. Victoria University, Wellington, New Zealand. 15 March 2015.\\
\years{2015$^t$} {\bf J. Bulbulia} and C. G. Sibley, What is the Dollar Value of Religion? Society of Australian Social Psychology Conference. Newcastle, Australia. 10 April 2015.\\
\years{2014$^t$} G. Troughton, {\bf J. Bulbulia}, D. Osborne, L. Greaves, Y. Huang, P. Milojev, and C. G. Sibley, Religion in Contemporary New Zealand: Insights from a National Probability Study. Combined Australian and New Zealand Religious History Conference. Massey University, Albany Campus. Massey University, Auckland, New Zealand. Wednesday 26 November 2014.  \\
\years{2014$^t$}  J. H. Shaver, C. G. Sibley, and {\bf J. Bulbulia}, Fast or Slow? Religion and Life History Strategies in New Zealand. IACSR panel, American Academy of Religion. San Diego, USA. Friday, 21 November 2014.\\
\years{2014$^t$}  {\bf J. Bulbulia}, J. H. Shaver, and C. G. Sibley, Are Religious People Really More Charitable? IACSR panel, American Academy of Religion. San Diego, USA. Friday 21 November 2014.\\
\years{2014$^t$} {\bf J. Bulbulia} and C. G. Sibley, The New Zealand Attitudes and Values Study: An overview. Presentation to Government:  Association of Social Science Research. 5 November 2014 \href{http://assr.org.nz/2014/11/22/the-new-zealand-attitudes-and-values-study-or-how-to-survive-starting-your-own-longitudinal-s-ample/}{link} \\
\years{2014$^t$}{\bf J. Bulbulia}, G. Troughton, and C. G. Sibley, Charity and Religion in New Zealand: The New Zealand Attitudes and Values Study. Laidlaw Theological Seminary. Auckland, New Zealand. 11 September 2014. \\
\years{2014$^t$}{\bf J. Bulbulia} and C. G. Sibley, The New Zealand Attitudes and Values Study: How to Survive a Longitudinal National Probability Sample. LEVYNA, Masaryk University. Brno, Czech Republic. 24 June 2014.\\
\years{2014$^t$}D. Xygalatas and {\bf J. Bulbulia}, Integration in the Cognitive Science of Religion: Methods, Theories, and People. IACSR Conference. Brno, Czech Republic. 21 June 2014. \\
\years{2014$^t$} {\bf J. Bulbulia},  Why Painful Rituals? Philosophy Workshop. Victoria University, Wellington, New Zealand. \\
\years{2013$^t$}{\bf J.~Bulbulia}, Quantifying Ritual Emotion. Victoria University Psychology Seminar. Victoria University, Wellington, New Zealand. 19 July 2013.\href{https://www.dropbox.com/s/nikzacfqpbypcd5/Bulbulia_19_July_VICPSYCH_poster.pdf}{poster}\\ Latex file:\href{https://www.dropbox.com/s/xeejz4jxfprsme0/Bulbulia_19_July_VICPSYCH_poster.tex}{here}\\
\years{2013$^t$}{\bf J.~Bulbulia}, Bayesian Analysis of Rated Images From a
Sacred Ritual Shows Role-Dependent Responses. Invited Poster. University of British Columbia CERC meeting. Vancouver, Canada. 5 May 2013.\href{https://www.dropbox.com/s/clkbjqcdqwhj213/Bulbulia_etal_poster_portrait_UBC_4_MAY_13.pdf}{poster}\\
\years{2013$^t$}{\bf J.~Bulbulia}, Faith After the Quake. Religious Studies Seminar. Wellington, New Zealand. 15 March 2013.\\
\years{2012$^t$}{\bf J.~Bulbulia}, Rituals, Pain, and Cooperation. The Elowitz Lab, California Institute of Technology, Biology Division. 22 November 2012.\\
\years{2012$^t$}{\bf J.~Bulbulia} and C. G. Sibley, How Religion Interacts with Personality to Affect Social Cognition. American Academy of Religion Conference. Chicago, USA. 18 November 2012.\href{https://www.dropbox.com/s/da5n8y0afhst554/18NOV_BULBUBULIA_AAR_2012.pdf}{pdf}\\
\years{2012$^t$}{\bf J.~Bulbulia}, Five Predictions For The Next Fifteen Years In The Experimental Study of Religion, Homo Experimentalis, LEVYNA. Masarky University, Brno, Czech Republic. 24 October 2012.\\
\years{2012$^t$}{\bf J.~Bulbulia}, J. Watts, Q. D. Atkinson, S. Greenhill, and R. Gray. Three Big Questions Cultural Phylogenetics Has Helped Historians to Answer. Society of Biblical Literature. Chicago, USA. 17 November 2012.\\
\years{2012$^t$}{\bf J.~Bulbulia}, Why Rituals? Results from experimental field studies. Language and Cultural Evolution Group. Auckland University. 12 October 2012.\\
\years{2012$^t$}{\bf J.~Bulbulia}, Plenary session report: The Cultural Evolution of Religion. Ernst Str\"ugnman Forum: \href{http://www.esforum.de/forums/esf12_cultural_evolution.html}{Cultural Evolution}. Frankfurt, Germany. 1 June 2012\\
\years{2012$^t$}{\bf J.~Bulbulia}, Subtractive and Additive Conceptions of Experimental Ritual Studies. Laboratory for the Experimental Study of Religion, Department for the Study of Religions. Masaryk University, Brno, Czech Republic. 9 January 2012.(Webinar)\\
\years{2011$^t$}{\bf J.~Bulbulia}, P. Reddish, R. Callander, and R. Fischer,  \newblock \href{http://db.tt/H0POMYBN}{Differential Effects on Cooperation from Rituals Varying in Body Synchrony and Sacred Values}\newblock AAR Cognitive Science of Religion Group. San Francisco, USA. 20 November 2011.\\
\years{2011$^t$}{\bf J.~Bulbulia}, P. Reddish, R. Callander, and R. Fischer, \newblock \href{http://www.psych.auckland.ac.nz/uoa/home/about/news-and-events/events/events/template/event_item.jsp?cid=362664}{Explaining collective rituals.}\newblock (invited talk): Auckland Psychology Department. 21 September 2011.\\
\newblock http://necsi.edu/events/iccs2011/accepted.html \newblock \href{https://www.dropbox.com/s/iqukoqbxzc7rzci/ICCS-259-FreanBulbulia.pdf}{PDF}\\
\years{2011$^t$}P. Reddish, R. Fischer and \textbf{J. Bulbulia},  Assessing the Cooperative Effects of Ritual Interactions: Synchrony or Choreography? Conference: The Cognitive Science Society/IACSR Workshop: New developments in the cognitive science of religion. Boston MA, USA. 20 July 2011.\\
\years{2010$^t$}{\bf J.~Bulbulia},
	\newblock Evolutionary cognitive science of religion.
	\newblock Conference: IAHR. Toronto, Canada. 19 August 2010.\\
\years{2010$^t$}\textbf{J.~Bulbulia}, P.~Reddish, R. Callander, and R.~Fischer, Explaining effervescence. Conference: IAHR. Toronto, Canada. 19 August 2010.\\
\years{2010$^t$}\textbf{J.~Bulbulia} and M.~Frean, Religious cooperation in large social worlds. Conference: IAHR. Toronto, Canada. 17 August 2010.\\
\years{2010$^t$}{\bf J.~Bulbulia}, Animal magnetism and social prediction. Conference: Toward a Unified Science of Religion. Otago University, Dunedin, New Zealand. 12 February 2010.\\
\years{2010$^t$}{\bf J.~Bulbulia}, Coordination at scale: the cooperative affordances of religious rituals. Adaptive Logic Group. Santa Barbara, California, USA. 9 January 2010.\\
\years{2009$^t$}{\bf J.~Bulbulia}, Cognitive study of religion: perspectives from social cognition. University of Vermont: Burlington Vermont, USA. 11 November 2009.\\
\years{2009$^t$}{\bf J.~Bulbulia}, The neuroeconomics of religion. AAR Cognitive Science of Religion Group. Montreal Quebec, Canada. 7 November 2009.\\
\years{2009$^t$}{\bf J.~Bulbulia}, The evolutionary study of religion: a primer. AAR Panel: evolution of Religion. Montreal Quebec, Canada. 8 November 2009.\\
\years{2009$^t$}{\bf J.~Bulbulia}, Explanation in the study of religion: the role of evidence~\&~models. Aarhus University, Religion Cognition and Culture. Aarhus, Denmark. 20 August 2009.\\
\years{2009$^t$}\textbf{J.~Bulbulia} and D.~Xygalatas,
  \href{http://www.interacting-minds.net/Sted/IM-SEMINAR2009.html}{Evidence of Emotional but not Perceptual Episodic Memory in a Spanish Firewalk}. Aarhus University, Center for Integrated Neuroscience. Aarhus, Denmark. 17 August 2009\\
\years{2009$^t$}{\bf J.~Bulbulia}, Evolving religious coordination through cues. Association for the Study of Religion and Economics. Washington D.C., USA. 3 April 2009.\\
\years{2009$^t$}\textbf{J.~Bulbulia} and D.~Xygalatas, Firewalking and the evolutionary theory of games. Society for Scientific Anthropology. Asilomar California, United States. 28 March 2009.\\
\years{2009$^t$}{\bf J.~Bulbulia}, Collective effervescence. Center for the Advanced Study in the Behavioral Sciences at Stanford University. Stanford University, Palo Alto California, United States. 30 March 2009.
\\
\years{2008$^t$}{\bf J.~Bulbulia},
\newblock Anthropomorphism and solidarity.
\newblock Biblical Literature and Biblical Religions. Auckland, New Zealand. August 2008.\\
\years{2008$^t$}{\bf J.~Bulbulia}, \newblock Religious signalling in a firewalk.\newblock Australian National University, Philosophy Programme RSSS: Biological Signaling workshop. \newblock Canberra,  Australia. 25 July 2008.\\
\years{2007$^t$}{\bf J.~Bulbulia}, \newblock Religion as coordination: Variable religious frames and the stag hunt.\newblock Association for the Study of Religion and Economics. Tampa Florida, USA. 3 November 2007.\\
\years{2007$^t$}{\bf J.~Bulbulia}, \newblock Religious schmelief: Religiosity as skilfull social engagement.
\newblock Society for the Scientific Study of Religion. 
\newblock Tampa Florida, USA. 4 November 2007.\\
\years{2007$^t$}{\bf J.~Bulbulia},
\newblock Religious altruism: results of an economic game.
\newblock Aarhus University, Aarhus, Denmark. 31 May 2007.\\
\years{2007$^t$}{\bf J.~Bulbulia},
\newblock The commitments of commitment signalling theory.
\newblock Hawaii Conference on Evolution and Religion. Makaha Resort Hawaii, USA. 6 January 2007.\\
\years{2006$^t$}{\bf J.~Bulbulia},
\newblock Why evolutionary niche construction matters to evolutionary understandings of religion.
\newblock University of Copenhagen, Copenhagen, Denmark. 14 December 2006.\\
\years{2006$^t$}{\bf J.~Bulbulia},
\newblock Constructing the schizophrenic niche: Cognitive adaptations for religious culture (featured speaker).
\newblock Evolution and Religion Workshop, Institute for Cognition and Culture. Queens University Belfast, Northern Ireland. 30 October 2006.\\
\years{2006$^t$}{\bf J.~Bulbulia},
\newblock Religious cognition, social cognition, and moral niche construction.
\newblock Danish Society for Philosophy of Psychology. Copenhagen, Denmark. September 2006.\\
\years{2006$^t$}{\bf J.~Bulbulia},
\newblock The cognitive origins of religion: what cultural inheritance does not explain.
\newblock International Association for the Cognitive Science of Religion. Aarhus, Denmark. January 2006.


% EXTERNAL FUNDING TO SELF SINCE 2012 AS PRIMARY 1,413,816
% TOTAL
\subsubsection*{Grants}
\noindent
\years{2018}J. Bulbulia (PI): {\bf Quantifying the dynamic interplay between virtue and human flourishing: a national-scale longitudinal study, USD NZD 4,596,114}.\\
\years{2017}  J. Bulbulia (consultant): {\bf High Fertility and Child Flourishing: The Success of Religions, USD 82,404.}\\
\years{2016}  J. Bulbulia (consultant): {\bf The Religious Replication Project: Using Pre-registered Replications and Bayesian Statistics to Improve the Experimental Study of Religion, USD 215,000}.\\
\years{2016}  J. Bulbulia (AI), Justin McBrayer Fort Lewis College USA (PI), {\bf Explaining Religion: A Planning Grant, NZD 208,343.15.}\\
\years{2013}  J. Bulbulia (PI), RSNZ Marsden: {\bf The Social Consequences of Religion, NZD 769,000.} \\
\years{2013}  J. Bulbulia (PI), C. G. Sibley (PI), and G. Troughton (AI). Templeton World Charity Foundation: {\bf The Personal Consequences of Religion, NZD 614,816.} \\
\years{2013} J. Bulbulia (PI), R. Fischer, P. Singh, S. Tewari, and R. Weiss.
\newblock  New Zealand India Research Institute: {\bf The interplay between religion, community making, and well-being, NZD 30,000.}\\
\years{2012} J. Bulbulia. \newblock:Center for Theological Inquiry, Princeton NJ: {\bf The Reverend Bayes Meets Charles Darwin visiting fellowship, USD 31,000.} [Offered: not accepted owing to family reasons].\\
\years{2012$\to$2014}R. Gray (PI), S. Greenhill (PI), J. Bulbulia (AI), and Q. D. Atkinson (AI). Sir John F. Templeton Foundation: {\bf The functional role of religion in the evolution of human society: NZD 393,330.60.}\\
\years{2012$\to$2014} R. Gray (PI), S. Greenhill (PI), and J. Bulbulia (AI). RSNZ Marsden:
{\bf The Cultural Evolution of Religion: NZD 775,000.}\\
\years{2012} J.~Bulbulia~(PI) and R. Fischer (AI). Victoria University URF:
{\bf Experimental Studies of Ritual Solidarity: NZD 40,000.}

\years{2011$\to$2013} W. McCorkle (Director), D. Xygalatas (Director), J.Bulbulia~(PI).
Czech Ministry of Education, Youth and Sports. \href{http://www.levyna.cz/team/}{LEVYNA: Laboratory for the Experimental Study of Religion, Department for the Study of Religions at Masaryk University, Brno, Czech Republic}{\bf: \euro~1,100,000}


%%\years{2009$\to$} F. Krueger (PI), J.~Bulbulia~(AI).
%%\newblock  NINDS: NIH {\bf Warfighter Head Injury Study Cognitive Neuroscience Section}.


\years{2009} J.~Bulbulia (AI).
\newblock Aarhus University, MindLAB, Denmark: {\bf Housing and accommodation grant, NZD 5,000.}\\
\years{2009} J.~Bulbulia~(PI) and M.~Frean (AI). Victoria University URF: {\bf The evolutionary dynamics of religious culture: NZD 17,000.}\\
\years{2008}J.~Bulbulia~(AI), J. Aarhus University, MindLAB, Denmark: {\bf Interacting Minds, Travel Grant: NZD 4,000}.\\
\years{2008} J.~Bulbulia~(AI), J.
\newblock European Science Foundation: {\bf ESF Travel and Accommodation Grant: NZD 6,000}.\\
\years{2007} R.~Sosis~(PI), J.~Bulbulia~(AI), G.~P. R, and C.~Genet.
\newblock Sir John F. Templeton Foundation: {\bf JFT Grant: Hawaii Evolution and Religion Conference: USD 30,000}.\\
\years{2006} J.~Bulbulia.
\newblock Aarhus University, Religion, Cognition, Culture. Denmark.
{\bf Guest Professor, Religion Cognition and Culture: NZD 80,000}.




\subsubsection*{Service}

\subsection*{Professional}
\years{2012}Ernst Strugmann Forum: Cultural Evolution (Religion) Rappourteur. 26 May--1 June, 2012.\\
%\years{2012$\to$}Editorial Advisory Board: \href{http://www.zygonjournal.org/board_ed_adv.html}{Zygon: Journal of Science and Religion}\\
%\years{2011$\to$}Editorial Advisory Board: \href{http://www.equinoxpub.com/index.php/JCSR}{Journal of The Cognitive Science of Religion}\\
%\years{2010$\rightarrow$}Editorial board, Religion Brain and Behavior.\\
\years{2008$\rightarrow$}Steering committee, \href{http://www.aarweb.org/Meetings/Annual_Meeting/Program_Units/PUinformation.asp?PUNum=AARPU173}{Cognitive Study of Religion Group, American Academy of Religion}.\\
\years{2008$\rightarrow$2010}Co-chair, Explanation, International Association for the History of Religions Conference. Toronto, Canada. 2010.\\
\years{2006$\rightarrow$} International Fellow, Religion Cognition and Culture. Aarhus University.\\
\years{2006$\rightarrow$2010} Member, Faculty of Humanities and Social Sciences Research Committee.\\



\subsubsection*{Victoria}

\years{2015$\rightarrow$} Religious Studies Seminar Series.\\
\years{2011$\rightarrow$} Convener and Chair, Animal Ethics Committee, Victoria University.\\
\years{2008$\rightarrow$2015} Honours Coordinator, Religious Studies, Victoria University.\\
\years{2006$\rightarrow$2010} Faculty of Humanities and Social Sciences Research Committee. \\
\years{2003$\rightarrow$2008} School Marketing Committee.\\
\years{2001$\rightarrow$2005} Programme Library Liaison.


\subsubsection*{Referee}
\begin{description}
\item  Asian Journal of Social Psychology
\item  Behavior and the Brain Sciences
\item  Biology and Philosophy
\item  Bloomsbury Press
\item  Cambridge University Press 
\item  Cognition
\item  Current Anthropology
\item  Evolution and Human Behavior
\item  Evolutionary Psychology
\item  Human Nature
\item  Journal of Economic Psychology
\item  International Journal of Intercultural Relations
\item  International Journal for the Psychology of Religion
\item  Israel Journal of Ecology and Evolution (IJEE)
\item  Journal of the American Academy of Religion
\item  Journal of Cognition and Culture
\item  Journal of Cross Cultural Psychology
\item  Journal for the Cognitive Science of Religion
\item  Oxford University Press
\item  PLoS One
\item  Proceedings of the National Academy of Sciences
\item  Religion
\item  Religion, Brain \& Behavior
\item  The Quarterly Review of Biology
\end{description}
\end{document}



